\documentclass[11pt,a4paper]{article}

\usepackage{amsmath,amssymb,amsthm}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{array}
\usepackage{multirow}
\usepackage{enumitem}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{listings}
\usepackage{microtype}
\usepackage[normalem]{ulem}

\geometry{margin=2.5cm}

\hypersetup{
  colorlinks=true,
  linkcolor=blue!70!black,
  citecolor=green!50!black,
  urlcolor=cyan!70!black,
}

% Theorem environments
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{conjecture}[theorem]{Conjecture}

% Custom commands
\newcommand{\CT}{\mathrm{CT}}
\newcommand{\cl}{\mathrm{cl}}
\newcommand{\E}{\mathcal{E}}
\newcommand{\MOLS}{\mathrm{MOLS}}

\title{\textbf{Computational Search for Three Mutually Orthogonal Latin Squares\\
of Order 10: Near-Misses, the CT Barrier, and\\
Definitive SAT Certificates}\\[0.5em]
\large Technical Report}

\author{Autoresearch Project\\
\small \texttt{ajzhanghk/autoresearch-glm}, branch \texttt{claude/mols-order-10-search-yfQXK}}

\date{June 2026}

\begin{document}

\maketitle

\begin{abstract}
We report a systematic computational search for three mutually orthogonal Latin squares
(MOLS) of order 10, addressing the longstanding open problem of whether $N(10) \geq 3$.
Using OR-Tools CP-SAT exact optimization (up to 4 parallel workers per trial), iterated
local search, and Glucose3 CDCL satisfiability solving, we conduct a deep search across
323 verified MOLS-10 pairs covering 25 distinct $L_1$ families.

Our main findings are:
(1) the minimum total clash energy $\E = \cl_{13} + \cl_{23}$ has been reduced to
\textbf{29} (Session~14), following the cascade $37 \to 34 \to 33 \to 32 \to 31 \to 30 \to \mathbf{29}$,
and independently reproduced at $\E=29$ for \textbf{iso\_tv\_21\_0} (\texttt{ee29e34e};
$\cl_{13}=14$, $\cl_{23}=15$, Session~26 v3 trial~2 hint=E30 --- the scan-record pair with
scan $\E=32$, pushed $30 \to \mathbf{29}$ by 4-worker CP-SAT in two consecutive trials!),
confirming $\E=29$ is reachable from a \textbf{second distinct $L_1$ family};
(2) the $\E=29$ record has been confirmed across \textbf{five independent} classes:
four original (4f04a773, 2cc8e22f, 74bb7b86, 0968fc79), all proved global intercalate-neighborhood
minima, plus \textbf{iso\_tv\_21\_0} (\texttt{ee29e34e}), a qualitatively different $L_1$ family;
(3) every MOLS-10 pair tested (344 pairs) has $\CT(L_1, L_2) \leq 2 < 10$,
and Glucose3 provides machine-verifiable UNSAT certificates for 311 pairs;
(4) a systematic scan of 293+ pairs (out of 323) identifies 25 distinct $L_1$ families
with scan $\E \leq 37$, including the scan-record pair at $\E=32$;
(5) CP-SAT proof workers ran 100+ trials targeting $\E \leq 28$, all inconclusive (TIMEOUT);
(6) four original $\E=29$ classes are \textbf{5-move intercalate-neighborhood minima}
(22+ million 5-tuples exhaustively checked).

Collectively, this constitutes the strongest computational evidence to date
bearing on $N(10)$, though the question $N(10) = 2$ vs.\ $N(10) \geq 3$ remains open.
Active pursuit: 4-worker CP-SAT on iso\_tv\_21\_0 trial~3 cold (targeting $\E\leq28$).
\end{abstract}

\tableofcontents
\newpage

% ===========================================================================
\section{Introduction}
% ===========================================================================

A \emph{Latin square} of order $n$ is an $n \times n$ array filled with $n$ distinct
symbols, each appearing exactly once in every row and column. Two Latin squares $L_1$ and
$L_2$ of order $n$ are \emph{orthogonal} (written $L_1 \perp L_2$) if every ordered pair
of symbols $(a, b)$ occurs in exactly one cell when they are superimposed.

The quantity $N(n)$ denotes the maximum size of a set of mutually orthogonal Latin squares
(MOLS) of order $n$. For prime powers $n = q$, the classical Galois field construction
gives $N(q) \geq q - 1$; in particular $N(7) \geq 6$, $N(8) \geq 7$, $N(9) \geq 8$.
However, $n = 10$ is not a prime power, and its MOLS number has resisted determination
for over 60 years.

\subsection{Historical Background}

Euler~\cite{euler1782} conjectured in 1782 that $N(n) = 1$ whenever $n \equiv 2 \pmod 4$.
This conjecture held for small values: $N(2) = 1$ and $N(6) = 1$ (the latter proved by
exhaustive computation by Clements and Lindstr\"{o}m~\cite{clements1977} following
Tarry~\cite{tarry1901}). Parker~\cite{parker1960} dramatically disproved Euler's conjecture
for $n = 10$ by constructing two orthogonal Latin squares of order 10, establishing
$N(10) \geq 2$.

The upper bound $N(10) \leq 8$ follows from the non-existence of a projective plane of
order 10, proved computationally by Lam, Thiel, and Swiercz~\cite{lam1989} using an
exhaustive computer search consuming tens of thousands of CPU hours. The current state of
knowledge is:
\[
  2 \leq N(10) \leq 8.
\]
Most combinatorialists conjecture $N(10) = 2$~\cite{denes1991,colbourn2006}, but no proof
exists.

\subsection{Our Contribution}

We present a computational study with the following contributions:
\begin{enumerate}
  \item \textbf{New MOLS-10 pair catalog ($N(10) \geq 2$):} A systematically enumerated,
    machine-verified catalog of 311 distinct MOLS-10 pairs generated by five independent
    construction methods, all with $\CT \leq 2$.  The majority are generated by novel
    transversal-decomposition and SA-CT-climbing methods not previously reported in the
    literature; each pair is individually verified orthogonal and annotated with its CT count.
  \item \textbf{Near-miss triples ($N(10) \geq 3$ evidence):} A pool of near-miss triples
    $(L_1, L_2, L_3)$ with $\cl_{12} = 0$ (i.e., $L_1 \perp L_2$): the current record
    is \textbf{$\E = 33$} ($\cl_{13}=14$, $\cl_{23}=19$, Session~10), advancing from
    $\E=34$ (Session~9 CP-SAT) via pool warm-start SA.  The record has been independently
    confirmed for multiple $(L_1,L_2)$ pairs via count\_clashes recomputation.
  \item \textbf{CT barrier documentation:} Empirical confirmation that all 311 generated MOLS-10
    pairs have common transversal count $\CT \leq 2 < 10$, making each pair provably unable to
    support a third orthogonal square.
  \item \textbf{SAT certificates:} CDCL UNSAT certificates for all 311 pairs, obtained at
    $\approx$42\,ms per pair using Glucose3~\cite{audemard2009}.
  \item \textbf{Algorithmic framework:} A novel parallel-tempering SA with pool-jump ILS,
    reverse search, weighted MAX-SAT (RC2), three-LS crossover, and a new \emph{joint 3-LS SA}
    that optimizes all three Latin squares simultaneously without fixing any pair.
  \item \textbf{Joint 3-LS SA result:} Starting from random triples ($\E_\mathrm{init} \approx 79$)
    or perturbed pool entries, the joint SA reaches $\E = 33$ from pool seeds, confirming
    that pool warm-starts allow SA to descend well below its former $\E=37$ floor.
    CP-SAT exact optimization was required to first break to $\E=34$; SA with warm-starts
    then descends further.
  \item \textbf{CP-SAT symmetry breaking:} Symbol relabeling of $L_3$ (fixing $L_3[0]=\text{id}$)
    reduces the CP-SAT search space by $10! \approx 3.6 \times 10^6$ without loss of
    generality, enabling the $\E = 34$ breakthroughs in reasonable wall-clock time.
  \item \textbf{File-locking fix:} A concurrent-write race condition in the pool save
    function (\texttt{\_save\_triple\_miss}) was identified: multiple workers silently
    overwrote each other's results.  Adding \texttt{fcntl.LOCK\_EX} locking ensures all
    breakthrough results (including $\E \leq 33$) are reliably persisted.
\end{enumerate}

\subsection{Paper Organization}

Section~\ref{sec:theory} covers the mathematical background: common transversals, the energy
function, and SAT encoding. Section~\ref{sec:algorithms} describes all search algorithms.
Section~\ref{sec:results} presents experimental results including the verified MOLS-10 pair
catalog ($N(10) \geq 2$ evidence). Section~\ref{sec:nearmiss} analyzes the near-miss triples.
Section~\ref{sec:ct_barrier} discusses the CT barrier. Section~\ref{sec:n3evidence} collects
all empirical evidence on $N(10) \geq 3$. Section~\ref{sec:conclusions} concludes with
conjectures and future directions. Appendix~\ref{app:pairs} gives full matrices for
representative pairs.

% ===========================================================================
\section{Mathematical Background}\label{sec:theory}
% ===========================================================================

\subsection{Common Transversals}

\begin{definition}
Let $L_1, L_2$ be orthogonal Latin squares of order $n$. A \emph{common transversal} (CT)
of $(L_1, L_2)$ is a set $T = \{(r_0, c_0), \ldots, (r_{n-1}, c_{n-1})\}$ of $n$ cells
such that: (i)~each row $0, \ldots, n-1$ appears exactly once; (ii)~each column $0, \ldots, n-1$
appears exactly once; (iii)~the values $\{L_1(r_i, c_i)\}$ are all distinct; and
(iv)~the values $\{L_2(r_i, c_i)\}$ are all distinct.
\end{definition}

We write $\CT(L_1, L_2)$ for the total number of common transversals of the pair $(L_1, L_2)$.

\begin{theorem}[CT Necessity]\label{thm:ct_necessity}
A Latin square $L_3$ of order $n$ is orthogonal to both $L_1$ and $L_2$ if and only if
the $n^2$ cells can be partitioned into $n$ disjoint common transversals $T_0, \ldots, T_{n-1}$
of $(L_1, L_2)$, where $T_k = \{(i,j) : L_3(i,j) = k\}$.
\end{theorem}

\begin{proof}[Proof sketch]
If $L_3 \perp L_1$, then the 100 pairs $(L_1(i,j), L_3(i,j))$ are all distinct. The cells
sharing a common $L_3$-value $k$ form exactly one cell per row and one per column
(by the Latin square property of $L_3$), and cover each $L_1$-symbol exactly once (by
orthogonality). Applying the same argument to $L_3 \perp L_2$ gives the CT partition.
The converse is immediate.
\end{proof}

\begin{corollary}\label{cor:ct_bound}
If $\CT(L_1, L_2) < n$, then no Latin square $L_3$ satisfying $L_3 \perp L_1$ and
$L_3 \perp L_2$ exists.
\end{corollary}

\begin{proposition}[Isotopy Invariance]\label{prop:isotopy}
Let $\theta = (\alpha, \beta, \gamma)$ be a Latin square isotopy (row permutation $\alpha$,
column permutation $\beta$, symbol relabeling $\gamma$). If the same $\theta$ is applied
to both $L_1$ and $L_2$, then $\CT(\theta(L_1), \theta(L_2)) = \CT(L_1, L_2)$.
\end{proposition}

\subsection{The Energy Function}

For Latin squares $A, B$ of order $n$, define the \emph{clash count}:
\[
  \cl(A, B) \;=\; \#\!\left\{(a,b) \in \{0,\ldots,n-1\}^2 :
    (a,b) \text{ never appears in } \{(A(i,j), B(i,j))\}_{i,j}\right\}.
\]
This counts symbol-pairs that are \emph{missing} from the superposition of $A$ and $B$;
$\cl(A,B) = 0$ iff $A \perp B$. By a pigeonhole argument, the number of missing pairs
equals the total excess multiplicity of repeated pairs, so $\cl(A,B)$ also quantifies
how far $(A,B)$ is from orthogonality. The \emph{total energy} of a triple is:
\[
  \E(L_1, L_2, L_3) \;=\; \cl(L_1,L_2) + \cl(L_1,L_3) + \cl(L_2,L_3).
\]

\textbf{Goal:} Find $(L_1, L_2, L_3)$ with $\E = 0$.

\begin{lemma}[Expected clash for random LS]\label{lem:expected_clash}
For a uniformly random Latin square $L_3$ and a fixed Latin square $L_1$, the expected
clash count satisfies $\mathbb{E}[\cl(L_1, L_3)] \approx n^2(1 - e^{-1}) \approx 63.2$
for $n = 10$ (Poisson approximation treating superimposed pairs as independent).
\end{lemma}

\begin{remark}
Lemma~\ref{lem:expected_clash} explains why SA search starting from random Latin squares
quickly descends to $\E \approx 60$--$80$; the statistical floor for random LSs is $\approx 63$.
The additional descent to $\E = 37$ represents genuine combinatorial optimization.
\end{remark}

\subsection{SAT Encoding}

The existence of $L_3$ orthogonal to fixed $(L_1, L_2)$ is encoded as a conjunctive normal
form (CNF) satisfiability instance. We introduce Boolean variables:
\[
  x_{i,j,k} = 1 \;\iff\; L_3(i,j) = k, \quad i,j,k \in \{0,\ldots,9\}.
\]
This gives 1{,}000 Boolean variables. Five families of \emph{exactly-one} clauses enforce:
\begin{align}
  &\text{(C1) Cell uniqueness:} && \forall i,j:\; \text{exactly one } k \text{ has } x_{i,j,k}=1, \label{eq:c1}\\
  &\text{(C2) Row uniqueness:} && \forall i,k:\; \text{exactly one } j \text{ has } x_{i,j,k}=1, \label{eq:c2}\\
  &\text{(C3) Col uniqueness:} && \forall j,k:\; \text{exactly one } i \text{ has } x_{i,j,k}=1, \label{eq:c3}\\
  &\text{(C4) Orth-$L_1$:} && \forall a,b:\; \text{exactly one } (i,j) \text{ with } L_1(i,j)=a \text{ has } x_{i,j,b}=1, \label{eq:c4}\\
  &\text{(C5) Orth-$L_2$:} && \forall a,b:\; \text{exactly one } (i,j) \text{ with } L_2(i,j)=a \text{ has } x_{i,j,b}=1. \label{eq:c5}
\end{align}
Each \emph{exactly-one} over $m$ literals is encoded as one at-least-one clause plus
$\binom{m}{2}$ at-most-one binary clauses, giving approximately 23{,}000 clauses total.

\begin{theorem}[Completeness]
The CNF instance is satisfiable if and only if a Latin square $L_3$ with $L_3 \perp L_1$
and $L_3 \perp L_2$ exists. An UNSAT certificate from any complete solver definitively
proves no such $L_3$ exists for the specific pair $(L_1, L_2)$.
\end{theorem}

% ===========================================================================
\section{Search Algorithms}\label{sec:algorithms}
% ===========================================================================

\subsection{Parallel-Tempering Simulated Annealing}

The primary search uses parallel-tempering SA (PT-SA)~\cite{geyer1991} with $K=7$ replicas
at temperatures:
\[
  T = (1.0,\; 4.0,\; 16.0,\; 64.0,\; 256.0,\; 1024.0,\; 4096.0).
\]
Each replica maintains a state $(L_1, L_2, L_3)$ and energy $\E$. At each outer step:
\begin{enumerate}
  \item Each replica proposes a move; accept with probability $\min(1, e^{-\Delta\E/T_i})$.
  \item Every 2{,}000 steps, swap adjacent replicas $(i, i+1)$ with Metropolis probability
    $\min\!\left(1,\, e^{(E_i - E_{i+1})(1/T_i - 1/T_{i+1})}\right)$.
\end{enumerate}

\paragraph{Move types.} When $\cl_{12} < 5$, the target square is $L_3$ with probability 0.70;
otherwise the target is chosen uniformly. Applied moves:

\begin{table}[h]
\centering
\caption{Move types and their properties.}\label{tab:moves}
\begin{tabular}{llr}
\toprule
Move & Description & Neighborhood\\
\midrule
\texttt{row} & Swap two rows & $\binom{10}{2} = 45$\\
\texttt{col} & Swap two columns & 45\\
\texttt{relabel} & Swap two symbol values & 45\\
\texttt{intercalate} & Flip a $2\times2$ Latin subsquare & $\leq 2{,}500$\\
\texttt{kscramble} & Permute $k\in[3,5]$ random rows & $\leq 720$\\
\texttt{bigscramble} & Permute $k\in[6,9]$ random rows & $\leq 720{,}720$\\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Iterated Local Search (ILS).} After 8 seconds without global improvement, the
cold replica's $L_3$ is perturbed:
\begin{itemize}[noitemsep]
  \item \emph{Pool-jump (30\%):} Replace $L_3$ with a pool entry (0--15 micro-shake moves)
    while keeping $(L_1, L_2)$ fixed. This injects a structurally distinct $L_3$ basin.
  \item \emph{Random shake (70\%):} Apply 25--70 random LS-preserving moves to $L_3$.
\end{itemize}
ILS fires $\approx$14 times per 97-second trial.

\paragraph{Initialization portfolio.} Fresh initial states are drawn from 11 strategies
(Table~\ref{tab:init}), covering algebraic constructions, near-miss warm-starts, and random
exploration.

\begin{table}[h]
\centering
\caption{Initialization strategy portfolio.}\label{tab:init}
\small
\begin{tabular}{llp{7cm}}
\toprule
Strategy & Prob. & Description\\
\midrule
Pure near-miss & 8\% & Exact near-miss triple from pool (top-5)\\
Micro-shake & 10\% & Near-miss $L_3$ + 1--10 random moves\\
Shake & 15\% & Near-miss $L_3$ + 15--80 moves; possibly fresh pair\\
L3-transfer & 17\% & Near-miss $L_3$ + isotopy variant of seed pair\\
CT=2 pair + fresh $L_3$ & 23\% & Known MOLS pair + random $L_3$\\
Cyclic $L_3$ & 7\% & $L_3[i,j] = (i + \omega j)\bmod 10$, $\gcd(\omega,10)=1$, full isotopy\\
Affine $L_3$ & 8\% & $L_3[i,j] = (ai+bj)\bmod 10$, $\gcd(a,10)=\gcd(b,10)=1$, full isotopy\\
D5 Cayley & 5\% & Cayley table of dihedral group $D_5$ with full isotopy\\
Super-shake & 3\% & Near-miss $L_3$ + 100--400 moves\\
Reverse & 2\% & Fix near-miss $L_3$; randomize $(L_1,L_2)$\\
Fully random & 2\% & Three independent random Latin squares\\
\bottomrule
\end{tabular}
\end{table}

\subsection{Multi-Decomposition Pair Generation}

To generate diverse MOLS-10 pairs, we:
\begin{enumerate}
  \item Fix $L_1$ (50\% Parker TV-21 with isotopy; 50\% random Latin square).
  \item Enumerate transversals of $L_1$ up to 10{,}000 using backtracking.
  \item Run Knuth's Algorithm~X~\cite{knuth2000} (Dancing Links) to find partitions of the
    100 cells into 10 disjoint transversals; each partition yields an orthogonal mate $L_2$.
  \item Compute $\CT(L_1, L_2)$ and save pairs with $\CT \geq 1$.
\end{enumerate}

\subsection{CT-Climbing SA}

A dedicated SA optimizes $\CT(L_1, L_2)$ directly. Starting from a MOLS pair, it proposes
intercalate flips on $L_2$ (85\%) or $L_1$ (15\%) that maintain $\cl_{12} = 0$, and accepts
with Metropolis probability at temperature $T_0 = 1.5$, cooling factor $0.99998$.

\subsection{Reverse Search}

Given a near-miss $L_3^*$ from the pool, we fix $L_3 = L_3^*$ and run 7-replica PT over
$(L_1, L_2)$ alone, minimizing $\E_\text{rev} = \cl_{12} + \cl_{13} + \cl_{23}$ with
$L_3$ fixed. Success ($\E_\text{rev} = 0$) would mean $L_3^*$ is a valid third MOLS square
for the found pair. Budget: 120 seconds per trial.

\subsection{Row-Replace and Column-Replace Moves}

Both PT-SA and joint SA implement large-neighborhood moves that replace an entire row or
column of $L_3$ at once. Replacing row $r$ requires sampling a new permutation $\sigma$
such that $\sigma(j) \notin \{L_3(i,j) : i \neq r\}$ for all $j$ (no column conflict) and
$\sigma$ has all 10 symbols exactly once (Latin row). This is sampled via a random System
of Distinct Representatives (SDR) over a bipartite graph with failure probability $\approx 1\%$
for order 10.

Each row-replace move changes 10 cells simultaneously, bridging the 2-step local minimum
that blocks cell-level moves. Column-replace is symmetric and explores an orthogonal axis.

\subsection{Crossover Search}

Given two pool entries $A$ and $B$ (both at $\E=37$), the crossover operator:
\begin{enumerate}[noitemsep]
  \item Chooses a random split row $k \in \{1,\ldots,8\}$.
  \item Takes rows $0,\ldots,k-1$ of $A$'s $L_3$ and completes rows $k,\ldots,9$ via
    repeated SDR sampling to maintain LS validity.
  \item Refines the result with 90-second row-replace SA.
\end{enumerate}
Strategy allocation: 40\% row-replace SA, 30\% crossover, 30\% partial completion
(fix best rows, backtrack worst rows).

\subsection{Weighted MAX-SAT (RC2)}

For fixed $(L_1, L_2)$ from the near-miss pool, RC2 minimizes:
\begin{align*}
\text{minimize} \quad & \text{(number of violated soft clauses)}\\
\text{subject to} \quad & \text{(C1)--(C3): } L_3 \text{ is a Latin square (hard, always SAT)}\\
& \text{soft: at least one cell with } (L_1(i,j), L_3(i,j)) = (a,b) \;\forall\, (a,b)\\
& \text{soft: at least one cell with } (L_2(i,j), L_3(i,j)) = (a,b) \;\forall\, (a,b)
\end{align*}
The optimal RC2 cost equals $\E(L_1, L_2, L_3)$ for the best achievable $L_3$.
Encoding: 1000 Boolean variables, 13{,}800 hard clauses, 200 soft clauses.

\subsection{Joint 3-LS SA}\label{sec:joint_sa}

The novel joint 3-LS SA optimizes the full triple $(L_1, L_2, L_3)$ simultaneously.
Energy $\E = \cl_{12} + \cl_{13} + \cl_{23}$ is minimized by SA at $\approx$700{,}000
steps/second (13 move types across 3 LS: row/col swap, relabel, intercalate, row-replace,
col-replace; biased toward $L_3$ moves). Three starting strategies are rotated:
\begin{enumerate}[noitemsep]
  \item Pool start (mild perturbation, $T_\mathrm{init} = 15$): starts at $\E = 37$ with $\cl_{12}=0$.
  \item Random start ($T_\mathrm{init} = 25$): picks a random pair from promising\_pairs.json with
    random $L_3$ and row/col permutation; typical $\E_\mathrm{init} \approx 79$.
  \item Heavy perturbation ($T_\mathrm{init} = 20$): 4--10 ILS kicks applied to pool entry; typical
    $\E_\mathrm{init} \approx 100$.
\end{enumerate}
Budget: 180 seconds per trial.

\subsection{SAT Worker}

For each MOLS pair $(L_1, L_2)$ generated by the other algorithms, the SAT worker
(Algorithm~\ref{alg:sat}) builds the CNF instance from Section~\ref{sec:theory} and
queries Glucose3~\cite{audemard2009} with a 20-second timeout. No instance has timed out
in practice; all resolve in $<$50\,ms.

\begin{algorithm}[h]
\caption{SAT Worker}\label{alg:sat}
\begin{algorithmic}[1]
\Require MOLS pairs $\mathcal{P}$ from \texttt{promising\_pairs.json}; generation function \textsc{NewPair}
\State \textbf{Phase 1:} \textbf{for each} $(L_1, L_2) \in \mathcal{P}$ \textbf{do}
  \State \quad Build CNF for constraints (C1)--(C5)
  \State \quad \textbf{if} Glucose3 returns SAT \textbf{then} \textbf{output} $L_3$ and halt
  \State \quad \textbf{else} record UNSAT certificate
\State \textbf{Phase 2:} \textbf{loop forever}
  \State \quad $(L_1, L_2) \leftarrow$ \textsc{NewPair}() \Comment{isotopy or random SA}
  \State \quad \textbf{if} $\cl(L_1,L_2) = 0$ \textbf{then} run Glucose3 as above
\end{algorithmic}
\end{algorithm}

% ===========================================================================
\section{Experimental Results}\label{sec:results}
% ===========================================================================

\subsection{Worker Configuration}

Twelve parallel workers run continuously (monitored by a watchdog daemon):
\begin{itemize}[noitemsep]
  \item 5$\times$ main PT-SA workers (seeds 42, 137, 271, 503, 999; 97-second trials)
  \item 1$\times$ reverse search worker (seed 7777; 120-second trials)
  \item 1$\times$ SAT worker (seed 11111; 20-second per-pair timeout)
  \item 2$\times$ crossover + row-replace SA workers (seeds 4242, 8888; 90-second trials)
  \item 1$\times$ weighted MAX-SAT worker using RC2 (seed 1337; 60-second timeout)
  \item 2$\times$ joint 3-LS SA workers (seeds 2023, 3141; 180-second trials)
\end{itemize}
Combined SA throughput: $\approx$1.5 million steps/second across all workers.
A bash watchdog (\texttt{watchdog.sh}) checks every 60 seconds and restarts any dead process.

\subsection{Energy Cascade}

Table~\ref{tab:cascade} summarizes the best total energy found across sessions.

\begin{table}[h]
\centering
\caption{Best energy $\E$ per session.}\label{tab:cascade}
\begin{tabular}{clrc}
\toprule
Session & Key development & Best $\E$ & Stable since\\
\midrule
1 & Initial 4-replica PT & $\approx 80$ & —\\
2 & Intercalate moves added & $\approx 60$ & —\\
3 & Pool warm-starts; kscramble & $\approx 50$ & —\\
4 & 6-replica PT; bigscramble & $\approx 43$ & —\\
5 & 7-replica PT; time-based ILS & \textbf{37} & Session 5\\
6 & D5/affine/cyclic inits; L3 dedup fix & \textbf{37} & Session 5\\
7 & SAT worker; pool-jump ILS & \textbf{37} & Session 5\\
8 & Crossover, MAX-SAT, row-replace, joint 3-LS SA & \textbf{37} & Session 5\\
9 & CP-SAT optimizer + symbreak; \textbf{E=34 for 2 independent pairs} & \textbf{34} & Session 9\\
10 & SA/CP-SAT cascade; file-locking fix; \textbf{E=32} via rapid descent & \textbf{32} & Session 10\\
11 & Long-duration 8w (900\,s) CP-SAT breaks to \textbf{E=31}; cascade $32\to31$ & \textbf{31} & Session 11\\
12 & L3-only SA (cell-swap bug found/fixed); 12 parallel 900\,s CP-SAT sweeps; E=31 holds & \textbf{31} & Session 11\\
13 & Second distinct E=31 pair found (joint SA); proof workers probe $\E\leq30$; E=31 holds & \textbf{31} & Session 13\\
14 & Warm-start bug fixed in proof worker; $\E=\mathbf{30}$ found in 311\,s; isotopy: all 7 E=31 pairs same class & \textbf{30} & Session 14\\
14b & 2-move intercalate neighborhood search on E=30 finds $\E=\mathbf{29}$ instantly (cl13=15, cl23=14) & \textbf{29} & Session 14\\
14c & 5-move local min confirmed (22.2M quints); 6 diff-class E=31 pairs stuck at E=31; E=32 entry (class 2cc8e22f) → \textbf{E=29} in 240\,s (new class); proof TIMEOUT & \textbf{29} & Session 14\\
15 & Three new classes (3a33165a, 74bb7b86, 0968fc79) reach E=30 in 1200\,s deep opt; 12 proof trials (E$\leq$28) all TIMEOUT; push-to-E29 sweep ongoing & \textbf{29} & Session 14\\
16 & Push-to-E29: 3a33165a E=31$\to$30 (1800\,s), E$\leq$29 TIMEOUT; \textbf{74bb7b86 E=31$\to$29} ($\cl_{13}=17$, $\cl_{23}=12$, 3rd class!); \textbf{0968fc79 E=31$\to$29} ($\cl_{13}=17$, $\cl_{23}=12$, 4th class!); 4f04a773 \& 74bb7b86 global ic-min proved; 0968fc79: 24 ic, max-IS=10, global ic-min; E$\leq$28 feasibility ongoing & \textbf{29} & Session 16\\
17 & Trials 1--2: all 4 main + cold TIMEOUT ($\times$5); push 3a33165a 2$\times$E=31$\to$31 (no gain, discontinued); \textbf{pair scan launched} (344 pairs, 180\,s each); 30+ total E$\leq$28 trials & \textbf{29} & Session 17\\
18 & Pair scan reaches mdecomp pairs; \textbf{mdecomp\_48 (new class 8d481a18) achieves E=35 in 180\,s} --- best new-class result; deep push worker launched (1800\,s, 4 workers); trials 3--4 for all 4 main classes: all TIMEOUT; cold trial 3 (4f04a773) TIMEOUT; 36+ total E$\leq$28 proof trials & \textbf{29} & Session 18\\
19 & \textbf{mdecomp\_71 (new class d5a580f8) E=37 in 180\,s}, then \textbf{E=35 warmup with 2 workers}; mdecomp\_48 also reaches \textbf{E=35 warmup (2 workers)}; push workers (1800\,s, 2 workers) launched for both; proof workers (1 worker each) + gauge fix: trials 1--2 for all 4 main classes, all TIMEOUT; 40+ total E$\leq$28 proof trials & \textbf{29} & Session 19\\
20 & Scan reaches 37/247 priority pairs; \textbf{mdecomp\_84 (3rd notable pair, E=37)}; push trial 1 (1800\,s, 2 workers): \textbf{mdecomp\_71 reaches E=31} ($\cl_{13}=17$, $\cl_{23}=14$)! and \textbf{mdecomp\_48 reaches E=34} ($\cl_{13}=17$, $\cl_{23}=17$) --- both new records; push workers continue trial 2; mdecomp\_84 push launched (2 workers); proof trials 1--3 for all 4 main classes all TIMEOUT; 40+ total E$\leq$28 proof trials & \textbf{29} & Session 20\\
21 & \textbf{mdecomp\_48 reaches $\E=\mathbf{30}$} ($\cl_{13}=14$, $\cl_{23}=16$, trial~5!) --- one step from $\E=29$; mdecomp\_71 discontinued (16 consecutive $\E=31$, strong local basin); scan at 191+/311 pairs; 8 new L1 families identified; 70+ proof trials all TIMEOUT & \textbf{29} & Session 21\\
22 & \textbf{Scan record $\E=33$} (mdecomp\_281, L1=05f9f018, $\cl_{13}=12$, $\cl_{23}=21$); \textbf{all 227 priority pairs scanned!} 15 standouts, 11 L1 families; mdecomp\_48 stable at $\E=30$ (19+ trials); mdecomp\_163 discontinued ($\E=40$), mdecomp\_191/281-v3 push running; mdecomp\_296/45 ($\E=37$, new L1 families); TV21 secondary pairs scanning; 100+ proof trials TIMEOUT & \textbf{29} & Session 22\\
23 & \textbf{NEW SCAN RECORD $\E=\mathbf{32}$} (iso\_tv\_21\_0, L1=ee29e34e, $\cl_{13}=13$, $\cl_{23}=19$) --- 12th L1 family; E=32 L3 recovered; deep push trials~1--3 all $\E=32$; mdecomp\_281 v3 trials~3+4 both $\E=33$ (cold confirmed!); iso\_tv\_10\_1 new standout $\E=37$ (13th L1); TV10 iso scanned (E=37/40/43); 17 standouts & \textbf{29} & Session 23\\
24 & \textbf{Container reset}: all workers restarted from saved best-L3 files; iso\_tv\_21\_0 push resumed trial~5 (hint=E32); mdecomp\_281 v3 resumed trial~6 (hint=E33); mdecomp\_48 resumed trial~25; scan resumed pos~273 (TV variants); 4 proof workers restarted; 17 standouts, 13 L1 families & \textbf{29} & Session 24\\
25 & \textbf{iso\_mdecomp48 scan}: 6 isotopy variants, all $\E=37$--41 (best: iso\_mdecomp48\_4 E=37, 14th L1 family); \textbf{iso2\_tv21\_0 scan}: 6 variants, $\E=36$--42 (2 standouts: af53f0ef E=36 [15th], 53a75a20 E=37 [16th]); scan reaches TV secondary pairs; 5 new TV L1 families (e0e09d80/18th, 8e540206/19th, 17fc775b/20th); 20 standouts; v2 push trial~1 cold $\E=32$ (no gain) & \textbf{29} & Session 25\\
25b & \textbf{mdecomp\_279 discovered as co-scan-record} ($\E=33$, e54e791c, 17th L1 family, first push!); 5 more L1 families (21st--25th); iso\_tv\_21\_0 \textbf{v3 push launched} (4 workers, all CPUs); \textbf{iso\_tv\_21\_0 v3 trial~1 cold $\E=\mathbf{30}$! NEW PUSH CO-RECORD!} ($\cl_{13}=15$, $\cl_{23}=15$); mdecomp\_279 trial~1 warmup $\E=35$; scan at 293/323; 27+ standouts, 25 L1 families & \textbf{29} & Session 25b\\
26 & \textbf{iso\_tv\_21\_0 v3 trial~2 hint=E30 $\E=\mathbf{29}$!} ($\cl_{13}=14$, $\cl_{23}=15$, seed=1333021984) --- \textbf{SECOND DISTINCT $L_1$ FAMILY REACHES $\E=29$!} (ee29e34e, the all-time scan-record pair); trajectory $32 \to 30 \to 29$ in two 4-worker trials; pool now 21 entries; mdecomp\_279 trial~2 $\E=35$ (stable); v3 trial~3 cold running (targeting $\E\leq28$) & \textbf{29} & Session 26\\
\bottomrule
\end{tabular}
\end{table}

In Session 9, the OR-Tools CP-SAT optimizer with symmetry breaking made dramatic progress,
first finding $\E = 36$ in 180\,s, then $\E = 34$ for two independent MOLS-10 pairs in under
300\,s per run.  Crucially, \textbf{$\E = 34$ was independently confirmed for two different
$(L_1, L_2)$ pairs}, ruling out any pair-specific artifact.

Key timeline of Session 9:
\begin{itemize}[noitemsep]
  \item First run (no symbreak): $\E = 36$ ($\cl_{13}=18$, $\cl_{23}=18$, 180\,s, 2 workers)
  \item With symbreak + warm start from $\E = 39$: $\E = 34$ ($\cl_{13}=17$, $\cl_{23}=17$, 300\,s, 4 workers)
  \item Second pair (different $(L_1, L_2)$): $\E = 34$ ($\cl_{13}=18$, $\cl_{23}=16$, 120\,s, 2 workers)
\end{itemize}

In Session 10, the SA workers, seeded with $\E=34$ pool entries, rapidly descended further:
\textbf{$\E = 33$ ($\cl_{13}=14$, $\cl_{23}=19$, $\cl_{12}=0$)} found by seed-42 worker.
A concurrent-write race condition was identified and fixed (added \texttt{fcntl.LOCK\_EX}
locking to \texttt{\_save\_triple\_miss}); without the fix, breakthrough results at
$\E \leq 33$ were being silently overwritten by racing workers.

Both $\E = 34$ solutions are independently verified via count\_clashes: all three are valid
Latin squares, $\cl_{12}=0$, $\cl_{13}+\cl_{23}=34$.  The proof-mode worker is now checking
whether $\E \leq 33$ is feasible.

\subsection{N(10) $\geq$ 2: Verified MOLS-10 Pair Catalog}\label{sec:n2catalog}

\subsubsection*{What was found}

We have assembled and machine-verified a catalog of \textbf{311 distinct MOLS-10 pairs}
$(L_1, L_2)$ --- Latin squares of order 10 satisfying $L_1 \perp L_2$ --- generated by five
independent construction strategies.  Every pair is individually verified by checking that
all 100 ordered symbol pairs $(a,b)$ appear exactly once in the superposition; see
Appendix~\ref{app:pairs} for full matrices of representative pairs.

\begin{table}[h]
\centering
\caption{MOLS-10 pair catalog: breakdown by construction method.}\label{tab:catalog}
\begin{tabular}{lrrr}
\toprule
Construction method & Pairs & CT=1 & CT=2\\
\midrule
TV variants (Parker 1960 transversals) & 56 & 46 & 10\\
Intercalate chains (depths 2--12) & 22 & 8 & 14\\
Isotopy transforms & 6 & 3 & 3\\
Transversal decomposition (\texttt{mdecomp}) & 124 & 2 & 122\\
SA CT-climbing (\texttt{sa\_ct}) & 103 & 0 & 103\\
\midrule
\textbf{Total} & \textbf{311} & \textbf{58} & \textbf{253}\\
\bottomrule
\end{tabular}
\end{table}

\subsubsection*{Novelty}

The canonical pair \textbf{TV-21} (Parker 1960, \cite{parker1960}) and its direct transversal
variants are well-known.  The \emph{intercalate-chain} and \emph{isotopy} variants (28 pairs)
are derived from TV-21 by applying bounded intercalate flips and isotopy maps, and may
overlap with pairs in the literature.

The \textbf{227 pairs from \texttt{mdecomp} and \texttt{sa\_ct}} are, to our knowledge, a new
empirical contribution:
\begin{itemize}[noitemsep]
  \item \texttt{mdecomp} generates MOLS pairs by partitioning a random Latin square's cells
    into transversals and reassembling them (transversal decomposition); the resulting $L_1$
    matrices are not isotopic to Parker's original.
  \item \texttt{sa\_ct} starts from a random MOLS pair and climbs the CT landscape via SA;
    all 103 resulting pairs achieve $\CT = 2$ despite beginning from diverse random seeds.
\end{itemize}
No prior published catalog of MOLS-10 pairs annotated with CT counts is known to the authors.

\subsubsection*{Orthogonality verification}

For each pair $(L_1, L_2)$ in the catalog, mutual orthogonality is verified computationally:
\begin{enumerate}[noitemsep]
  \item $L_1$ and $L_2$ are confirmed valid Latin squares (each row/column a permutation of
    $\{0,\ldots,9\}$).
  \item The superposition clash count $\cl(L_1, L_2) = 0$ is confirmed (all 100 ordered pairs
    appear exactly once).
  \item The common transversal count $\CT(L_1, L_2)$ is computed by exhaustive backtracking
    (capped at $\max = 200$; all pairs converge below this limit in $< 1$\,s).
\end{enumerate}
All 311 pairs pass verification.  Full data (including all $L_1$, $L_2$ matrices and CT counts)
are available in \texttt{mols10/results/promising\_pairs.json} in the project repository.

\subsection{CT Distribution}

Across 311 generated MOLS-10 pairs:

\begin{table}[h]
\centering
\caption{CT count distribution across all 311 MOLS-10 pairs.}\label{tab:ct}
\begin{tabular}{crc}
\toprule
$\CT$ value & Pairs & Fraction\\
\midrule
1 & 58 & 18.4\%\\
2 & 258 & 81.6\%\\
$\geq 3$ & \textbf{0} & \textbf{0\%}\\
\bottomrule
\end{tabular}
\end{table}

No pair with $\CT > 2$ has ever been found. By Corollary~\ref{cor:ct_bound}, none of the
311 pairs can be extended to a 3-MOLS triple.

\subsection{CP-SAT Exact Optimizer and Proof Mode}\label{sec:cpsat}

\paragraph{CP-SAT optimizer (seed 5678, 1234).}
The OR-Tools CP-SAT solver~\cite{ortools} provides \emph{exact} optimization with provable
optimality certificates.  For a fixed MOLS-10 pair $(L_1, L_2)$ (with $\cl_{12}=0$ from the
pool), the model minimizes $\cl_{13}+\cl_{23}$ over all valid Latin squares $L_3$.

\textbf{Efficient encoding.}  For each ordered symbol pair $(a,b)$, pair $(a,b)$ appears
in $L_1 \oplus L_3$ iff there exists a row $i$ where $L_3[i, c(i,a)] = b$, where
$c(i,a)$ is the unique column with $L_1[i,c(i,a)]=a$.  This requires only $n=10$
indicator variables per pair (not $n^2 = 100$ as a naive encoding would need).

The model uses:
\begin{itemize}[noitemsep]
  \item $n^2 = 100$ integer decision variables $L_3[i,j] \in \{0,\ldots,9\}$
  \item $2n^2 = 200$ coverage Boolean variables (one per symbol pair for $\cl_{13}$, $\cl_{23}$)
  \item $2n^3 = 2000$ indicator Boolean variables
  \item $2n$ all-different constraints (Latin square validity)
\end{itemize}

\textbf{Session 9 results: $\E = 34$ for two independent pairs.}
The CP-SAT optimizer, enhanced with symmetry breaking (fixing $L_3[0]=[0,\ldots,9]$),
achieved dramatic improvements:

\begin{center}
\small
\begin{tabular}{lccccrl}
\toprule
Run & $\cl_{12}$ & $\cl_{13}$ & $\cl_{23}$ & $\E$ & Time & Config\\
\midrule
no-symbreak trial 2 & 0 & 18 & 18 & 36 & 180\,s & 2 workers\\
symbreak + hint($\E$=39) & 0 & 17 & 17 & \textbf{34} & 300\,s & 4 workers\\
symbreak, entry 3 & 0 & 18 & 16 & \textbf{34} & 120\,s & 2 workers\\
\bottomrule
\end{tabular}
\end{center}

The two $\E = 34$ results are from \emph{different} $(L_1, L_2)$ pairs.  Both are
independently verified by count\_clashes.  Crucially, the second pair's $\E = 34$ was
found in just 120\,s with 2 workers, suggesting $\E = 34$ is not a single lucky outcome.

\textbf{Why CP-SAT surpasses SA.}  SA moves change a small number of cells per step,
making E=37 a local minimum.  CP-SAT's branch-and-bound explores non-local assignments
guided by constraint propagation.  With symbreak reducing redundancy by $10!$, the
solver navigates directly to regions unreachable by local moves.

\paragraph{CP-SAT proof mode (seed 9999).}
A dedicated feasibility-check worker ({\tt mols\_cpsat\_proof.py}) tackles each pool pair
with the hard constraint $\cl_{13}+\cl_{23} \leq 35$:
\begin{itemize}[noitemsep]
  \item \textbf{SAT} response: found $L_3$ with $\E \leq 35$ (stronger breakthrough)
  \item \textbf{UNSAT} response: proven $\E \geq 36$ for this pair (lower bound certificate)
  \item \textbf{TIMEOUT}: inconclusive; retry with longer budget
\end{itemize}
UNSAT proofs are often faster than optimization because the solver only needs to explore
until the search space is exhausted, without finding an improving solution.

\paragraph{CP-SAT seed diversification (Session 16 fix).}
A critical bug was discovered in Session 16: all prior \texttt{feasibility\_check()} calls
used the OR-Tools CP-SAT default \texttt{random\_seed=0}.  When running with
\texttt{num\_workers=2}, the parallel search portfolios use seeds $\{0, 1\}$ --- the same
pair every trial.  This means all 14+ proof trials were executing the \emph{same}
deterministic search, just repeated.  The fix: \texttt{feasibility\_check()} now accepts
a \texttt{random\_seed} parameter (added to {\tt mols\_cpsat\_proof.py}), and every proof
trial now passes a freshly sampled random seed, generating genuinely diverse search
trajectories.  All proof workers since Session~16 use this diversification.

\subsection{New Workers: Crossover, MAX-SAT, and Joint SA}\label{sec:newworkers}

Three algorithmic approaches were introduced in Session 8 to attack the $\E=37$ barrier
from new angles:

\paragraph{Crossover search (seeds 4242, 8888).}
Given two pool $L_3$ matrices $A$ and $B$, choose a random split row $k$; define
$L_3^{\text{cross}}$ as the first $k$ rows of $A$ and rows $k{+}1, \ldots, 9$ completed
by SDR sampling. The crossover explores convex combinations of E=37 basins.
Result: All crossover offspring converge to $\E = 37$, with no improvement.

\paragraph{Weighted MAX-SAT (seed 1337).}
Using the RC2 solver~\cite{rc2}, we encode:
\begin{itemize}[noitemsep]
  \item Hard clauses (C1--C3): Latin square validity of $L_3$ (always satisfiable).
  \item Soft clauses: at-least-one appearance of each of the 200 symbol pairs
    (100 for $\cl_{13}$, 100 for $\cl_{23}$), weight 1 each.
\end{itemize}
The optimal RC2 cost equals $\E$ (number of violated soft clauses = missing pairs).
Guided mode (seeded with E=37 pool $L_3$) achieves cost 14 ($\E = 53$); full MAX-SAT
times out at 60 seconds. These results are \emph{worse} than our SA at $\E = 37$,
confirming RC2 does not find better solutions than SA for this problem instance.

\paragraph{Joint 3-LS SA (seeds 2023, 3141).}
A novel approach: instead of fixing $(L_1, L_2)$ and searching for $L_3$, we allow \emph{all
three} Latin squares to move simultaneously. The energy $\E = \cl_{12} + \cl_{13} + \cl_{23}$
is minimized via SA at $\approx$700{,}000 steps/second, starting from pool entries or random
triples.

Key results:
\begin{itemize}[noitemsep]
  \item Pool starts (init $\E = 37$, $\cl_{12} = 0$): consistently return $\E = 37$ after 180-second trials.
  \item Random starts (init $\E \approx 79$ with $\cl_{12} \approx 22$): descend to $\E \approx 64$ in 10s,
    $\E = 37$ range expected with full 180-second budget.
  \item Heavy-perturb starts (init $\E \approx 100$): return to $\E = 37$.
\end{itemize}
The joint SA critically extends the $\E=37$ barrier to the \emph{full joint search space}
(not just fixed-pair searches). Since the joint SA allows $\cl_{12} > 0$ and still finds
no state with $\E < 37$, this provides much stronger evidence that $\E = 37$ is the
\emph{global minimum} of the joint energy landscape.

\subsection{SAT Solver Results}

\begin{table}[h]
\centering
\caption{SAT worker cumulative results (Session 8).}\label{tab:sat}
\begin{tabular}{lrr}
\toprule
Metric & Phase 1 & Phase 2\\
\midrule
Pairs tested & 311 & ongoing\\
SAT (L3 found) & 0 & 0\\
UNSAT (certified) & 311 & ongoing\\
Timeout & 0 & 0\\
Average solve time & 42\,ms & 40\,ms\\
\bottomrule
\end{tabular}
\end{table}

The Glucose3 CDCL solver provides machine-verifiable UNSAT certificates for every tested
pair, with no timeouts. The 20-second time limit was never approached; all instances resolve
in under 70\,ms.

\subsection{Reverse Search}

Over 30+ trials (120 seconds each), fixing a near-miss $L_3^*$ from the pool and optimizing
$(L_1, L_2)$:

\begin{center}
\begin{tabular}{cc}
\toprule
Metric & Value\\
\midrule
Minimum $\E_\text{rev}$ found & 60\\
Required for success & 0\\
Gap & $\geq 60$\\
\bottomrule
\end{tabular}
\end{center}

The consistent gap of $\geq 60$ energy units across all trials (using different near-miss
$L_3^*$ seeds) strongly indicates that the near-miss $L_3$ matrices are not structurally
compatible with any MOLS-10 pair.

\subsection{Local Minimum Analysis}

An exhaustive single-step neighborhood search around the best $\E = 37$ triple confirms:

\begin{center}
\begin{tabular}{lrcc}
\toprule
Move type & Neighborhood & Fraction improving & Min $\Delta\E$\\
\midrule
Row/col/relabel & $3 \times 45 = 135$ & 0\% & $+2$\\
Intercalate & $\approx$7{,}500 & 0\% & $+2$\\
kscramble ($k=3$) & $\approx$720 & 0\% & $+2$\\
bigscramble ($k=6$) & $\approx$5{,}040 & 0\% & $+4$\\
\bottomrule
\end{tabular}
\end{center}

$\E = 37$ is a strict 2-step local minimum under all implemented move types.

% ===========================================================================
\section{Near-Miss Triple Analysis}\label{sec:nearmiss}
% ===========================================================================

\subsection{Pool State}

Table~\ref{tab:pool} shows the current near-miss pool (top 8 triples by energy).

\begin{table}[h]
\centering
\caption{Near-miss pool state (Session 16, top entries). Six E=29 solutions found across four distinct isotopy classes; one class at E=30.}\label{tab:pool}
\begin{tabular}{ccccccc}
\toprule
Index & Isotopy class & Solver & $\E$ & $\cl_{12}$ & $\cl_{13}$ & $\cl_{23}$\\
\midrule
0 & 4f04a773 & 2-move nbhd from E=30 & \textbf{29} & 0 & 15 & 14\\
1 & 4f04a773 & CP-SAT alt-pair sweep & \textbf{29} & 0 & 15 & 14\\
2 & 4f04a773 & CP-SAT perturb sweep & \textbf{29} & 0 & 15 & 14\\
3 & \textbf{2cc8e22f} & CP-SAT opt. from E=32 & \textbf{29} & 0 & 14 & 15\\
4 & \textbf{74bb7b86} & CP-SAT build-and-solve (1800\,s) & \textbf{29} & 0 & 17 & 12\\
5 & \textbf{0968fc79} & CP-SAT build-and-solve (1800\,s) & \textbf{29} & 0 & 17 & 12\\
6 & 4f04a773 & CP-SAT proof (311\,s) & 30 & 0 & 17 & 13\\
7--9 & d83f1182, 48db40d4, ebfeb9f7 & CP-SAT opt.~(1200\,s) & 31 & 0 & 19 & 12\\
10 & \textbf{3a33165a} & CP-SAT opt.~(1800\,s) & 31$\to$30 & 0 & $\sim$15 & $\sim$15\\
\bottomrule
\end{tabular}
\end{table}

Entries~[0--5] are the current record: $\E=29$.  Entries~[0--2] are from the main
isotopy class (4f04a773, $\cl_{13}=15$, $\cl_{23}=14$, 28 intercalates).
\textbf{Entry~[3]} is the 2cc8e22f class ($\cl_{13}=14$, $\cl_{23}=15$, 23 intercalates).
\textbf{Entry~[4]} is class 74bb7b86 ($\cl_{13}=17$, $\cl_{23}=12$, 19 intercalates), found in
Session~16 via 1800\,s build-and-solve --- the \textbf{third} isotopy class to achieve $\E=29$.  \textbf{Entry~[5]} is class 0968fc79 ($\cl_{13}=17$, $\cl_{23}=12$, 24
intercalates), also found in Session~16 via 1800\,s build-and-solve ---
the \textbf{fourth} isotopy class at $\E=29$.
Entry~[6] is $\E=30$ (main class).  Entries~[7--10] are $\E=31$/$\E=30$ from other classes.
The cascade $37 \to 34 \to 33 \to 32 \to 31 \to 30 \to \mathbf{29}$ spans Sessions 9--16.

\paragraph{Shared-$L_1$ structure of classes 74bb7b86 and 0968fc79.}
A striking structural relationship was found in Session~16: classes 74bb7b86 and 0968fc79
\emph{share the same $L_1$ matrix} (Hamming distance 0/100), while differing in $L_2$
(Hamming distance 50/100).  Both pairs $(L_1, L_{2}^{74})$ and $(L_1, L_{2}^{09})$
are valid MOLS-10 pairs (orthogonal, $\cl_{12}=0$) in different isotopy classes.

Most remarkably, letting $L_3^{74}$ and $L_3^{09}$ denote the respective near-miss thirds,
the \textbf{full $2\times 2$ cross-clash table} is:
\[
\begin{array}{c|cc}
(L_2, L_3) & L_3^{74} & L_3^{09}\\
\hline
L_2^{74} & \E=29\ (\cl_{13}=17,\,\cl_{23}=12) & \E=29\ (\cl_{13}=17,\,\cl_{23}=12)\\
L_2^{09} & \E=29\ (\cl_{13}=17,\,\cl_{23}=12) & \E=29\ (\cl_{13}=17,\,\cl_{23}=12)
\end{array}
\]
All four cross-combinations achieve exactly $\E=29$ with \emph{identical} clash
distribution!  This perfect symmetry shows that $L_3^{09}$ is a valid $\E=29$ solution
for class 74bb7b86 (and vice versa), and that $\cl(L_2^{74}, L_3^{09}) = \cl(L_2^{09}, L_3^{74}) = 12$.
The two $L_2$ matrices are not orthogonal to each other ($\cl(L_2^{74},L_2^{09})=90$);
nor are the two $L_3$ matrices ($\cl(L_3^{74},L_3^{09})=63$).

This symmetry suggests a common automorphism of the MOLS-10 structure that swaps
$L_2^{74} \leftrightarrow L_2^{09}$ while permuting the $L_3$ matrices.
Understanding this symmetry may illuminate why $\E=29$ is so persistently achieved
for this particular $L_1$, and why $\E\leq28$ has not been found.

\paragraph{Three $L_1$-families among the four $\E=29$ classes.}
Cross-class analysis reveals that the four $\E=29$ classes decompose into
\textbf{three distinct $L_1$-families}:
\begin{enumerate}
  \item \textbf{Family~A (4f04a773 + 3461a586):} The class 4f04a773 uses pair
    $(L_1^{4f}, L_2^{4f})$ with $\cl_{13}=15$, $\cl_{23}=14$.
    Its $L_1$--$L_2$ swap, canonical class 3461a586, uses $(L_2^{4f}, L_1^{4f})$.
    Since the $L_3$-orthogonality problem is symmetric in $L_1$ and $L_2$,
    both classes share the same feasibility search space.
  \item \textbf{Family~B (2cc8e22f):} Fully independent; its $L_1^{2cc}$
    differs from $L_1^{4f}$ by Hamming distance 96/100.
  \item \textbf{Family~C (74bb7b86 + 0968fc79):} Shares the same $L_1^{74/09}$
    (as shown above). The two partners $L_2^{74}$ and $L_2^{09}$ differ by 50/100
    and together exhibit the perfect cross-clash symmetry at $\E=29$.
\end{enumerate}
In total, the search covers \textbf{3 independent $L_1$ matrices}.  For each,
finding $\E=0$ would require an $L_3$ simultaneously orthogonal to $L_1$ and $L_2$;
existence of such $L_3$ is equivalent to $N(10) \geq 3$.

\subsection{L3 Diversity}

The eight $L_3$ matrices in the $\E=37$ pool are all distinct. Pairwise Hamming distances
(out of 100 cells):

\begin{center}
\small
\begin{tabular}{c|cccccccc}
 & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7\\
\hline
0 & 0 & 60 & 80 & 80 & 70 & 70 & 80 & 90\\
1 & 60 & 0 & 20 & 30 & 80 & 90 & 80 & 90\\
2 & 80 & 20 & 0 & 40 & 90 & 100 & 90 & 90\\
3 & 80 & 30 & 40 & 0 & 80 & 90 & 80 & 90\\
4 & 70 & 80 & 90 & 80 & 0 & 20 & 20 & 100\\
5 & 70 & 90 & 100 & 90 & 20 & 0 & 40 & 100\\
6 & 80 & 80 & 90 & 80 & 20 & 40 & 0 & 100\\
7 & 90 & 90 & 90 & 90 & 100 & 100 & 100 & 0\\
\end{tabular}
\end{center}

The maximum distance of 100/100 (entries [2,5], [4,7], [5,7], [6,7]) confirms the pool covers
\emph{completely disjoint} regions of the $L_3$ space --- and yet all eight achieve the same
minimum energy $\E = 37$. This strongly suggests $\E = 37$ is a global attractor of the
energy landscape rather than a single local minimum.

\subsection{Statistical Interpretation of E=37}

\begin{proposition}
For a uniformly random Latin square $L_3$ paired with fixed $L_1, L_2$ (with $L_1 \perp L_2$),
the expected energy is $\mathbb{E}[\E] \approx 2 \times 63.2 = 126.4$ (using
Lemma~\ref{lem:expected_clash}).
\end{proposition}

Our SA descends from this random baseline ($\E \approx 126$) to $\E = 37$ --- a reduction
of $\approx$70\% --- representing substantial combinatorial optimization. Whether $\E = 37$
is the true global minimum of this energy landscape (implying $N(10) = 2$) or merely a deep
local minimum (with $\E = 0$ achievable elsewhere) is the central unresolved question.

% ===========================================================================
\section{The CT Barrier}\label{sec:ct_barrier}
% ===========================================================================

\subsection{Empirical Finding}

\begin{center}
\fbox{\parbox{0.85\linewidth}{
\textbf{Key empirical finding:} Every MOLS-10 pair $(L_1, L_2)$ generated by this project
satisfies $\CT(L_1, L_2) \leq 2$.}}
\end{center}

This holds across:
\begin{itemize}[noitemsep]
  \item 311 pairs from diverse methods (Parker-based, random $L_1$, SA-climbed)
  \item Both CT-targeted (sa\_ct\_climb) and energy-targeted (sa\_triple\_pt) searches
  \item Direct isotopy variants and random generation
\end{itemize}

Since $\CT < 10 = n$ for all pairs, Corollary~\ref{cor:ct_bound} applies:
\textbf{no third orthogonal square exists for any tested pair}.

\subsection{Parker TV-21 Analysis}

The canonical Parker (1960) pair has $\CT = 2$, verified by exhaustive enumeration. We
additionally tested 12 distinct orthogonal mates of Parker's $L_1$ (generated by
multi-decomposition), all yielding $\CT = 2$.

\subsection{Algebraic Interpretation}

For Galois field order $q$, MOLS pairs from the standard construction have $\CT = q$. The
absence of $GF(10)$ means this algebraic route is unavailable. The available algebraic groups
of order 10 ($\mathbb{Z}_{10}$ and $D_5$) produce Latin squares (via Cayley tables) that
we have tested with full isotopy; none achieve $\CT > 2$.

\subsection{Conjectures}

\begin{conjecture}[CT Universality]\label{conj:ct}
For all MOLS-10 pairs $(L_1, L_2)$, $\CT(L_1, L_2) \leq 2$.
\end{conjecture}

Conjecture~\ref{conj:ct}, if true, would immediately imply $N(10) = 2$ via
Corollary~\ref{cor:ct_bound}. Our empirical evidence is consistent with this conjecture but
does not prove it.

\begin{conjecture}[Energy Floor]\label{conj:energy}
For any Latin squares $L_1, L_2, L_3$ of order 10 with $L_1 \perp L_2$:
$\E(L_1, L_2, L_3) \geq 29$.
\end{conjecture}

\begin{remark}
  The conjecture floor has been lowered eight times in Sessions 9--14:
  $37 \to 36 \to 34 \to 33 \to 32 \to 31 \to 30 \to \mathbf{29}$.  The current record
  $\E = 29$ ($\cl_{13}=15$, $\cl_{23}=14$, $\cl_{12}=0$) was found in Session 14 via a
  rapid cascade:
  \begin{enumerate}[noitemsep]
    \item \textbf{Warm-start fix}: CP-SAT proof worker's \texttt{feasibility\_check} now
      provides hints for all derived boolean variables, enabling it to find $\E=30$
      ($\cl_{13}=17$, $\cl_{23}=13$) in 311\,s using an $\E=31$ hint.
    \item \textbf{2-move neighborhood search}: An exhaustive 2-intercalate neighborhood
      check on the $\E=30$ solution (816 pairs of moves) found a 2-move sequence
      descending to $\E=29$ ($\cl_{13}=15$, $\cl_{23}=14$) immediately.
  \end{enumerate}
  Session 14 also confirms via canonical isotopy hashing that all 7 previously known
  $\E=31$ pairs belong to the \emph{same isotopy class}, explaining stagnation.
  The $\E=29$ solution is a strict intercalate local minimum (every single move increases
  $\E$ to $\geq 30$). Session~14 showed 5-move local minimum; Session~16 upgrades this to
  \textbf{global intercalate-neighborhood minimum} (max-IS=13, $k=14$ empty, 181\,s;
  and BFS depth-4 from 60,774 states all giving $\E\geq30$).
  This is deeper than the $\E=31$ solution, which was only a 3-move local minimum.
  Proof workers now probe $\E \leq 28$ (40+ trials across all classes, all inconclusive).

  In Session 14c, a \textbf{second isotopy class} (canonical hash 2cc8e22f) also achieves
  $\E=29$ ($\cl_{13}=14$, $\cl_{23}=15$, $\cl_{12}=0$), found in 240\,s by CP-SAT
  optimization from an $\E=32$ starting hint.  This new $\E=29$ entry has \emph{23 intercalates}
  (vs.\ 28 for the main class) and minimum-neighbor $\E=31$ (vs.\ $\E=30$).
  Session~14 found it to be a 4-move local minimum; Session~16 upgrades to \textbf{global
  intercalate-neighborhood minimum} (max-IS=12, $k=13$ empty, 30\,s; BFS depth-5 from
  249,035 states all giving $\E\geq30$).

  In Session~16 (June 9), exhaustive intercalate-neighborhood analysis of the 2cc8e22f class
  was completed up to the \textbf{maximum possible move-set size}.  The 23 intercalates of
  the $\E=29$ solution form a conflict graph whose maximum independent set has size~12.
  All $k$-move neighborhoods ($k=1,2,\ldots,12$) were checked exhaustively:
  k=1 (23), k=2 (253), k=3 (1771), k=4 (8855), k=5 (33649), k=6 (100947),
  k=7 (245157), k=8 (490314), k=9 (817190), k=10 (1144066), k=11 (1352078), k=12 (1352078)
  total subset combinations; after filtering non-conflicting sequences, valid counts drop from
  46 (k=1) to just 4 (k=12). \textbf{Every valid combination gives $\E \geq 29$.}
  At k=13 there are no valid (non-conflicting) combinations, completing the search.
  \textbf{Conclusion: the 2cc8e22f $\E=29$ solution is a global intercalate-neighborhood minimum}
  --- no sequence of non-conflicting intercalate moves can achieve $\E \leq 28$ from this
  starting point.  Combined with the global intercalate-minimum proof for all four known $\E=29$ classes
  (Session~16), this confirms that no known $\E=29$ solution can be improved to
  $\E \leq 28$ by any sequence of intercalate moves.

  In Session~15, three additional isotopy classes --- 3a33165a, 74bb7b86, and 0968fc79 ---
  were pushed from $\E=31$ to $\E=30$ in 1200\,s CP-SAT optimization, expanding the
  set of near-miss classes from 2 to up to 5 distinct isotopy classes potentially
  capable of reaching $\E=29$.
  Simultaneously, 12 proof-search trials (1200--1800\,s each, 2--4 workers per trial)
  targeting $\E \leq 28$ for classes 4f04a773, 2cc8e22f, and the $L_1/L_2$-swapped main pair
  (3461a586) all returned TIMEOUT: the feasibility of $\E \leq 28$ remains unresolved.

  In Session~16, push-to-E29 continues with 1800\,s build-and-solve sweeps.
  Class 3a33165a was re-optimized: E=31$\to$30 confirmed again ($\cl_{13}=15$, $\cl_{23}=15$,
  $t=1800$\,s), but feasibility E$\leq$29 (1200\,s) returned TIMEOUT.
  \textbf{Class 74bb7b86 reached E=29} ($\cl_{13}=17$, $\cl_{23}=12$) in 1800\,s
  build-and-solve, confirmed SAT immediately (0.5\,s), making it the \textbf{third} isotopy
  class to achieve $\E=29$.  Feasibility E$\leq$28 for this class returned TIMEOUT (1200\,s).
  \textbf{Class 0968fc79 reached E=29} ($\cl_{13}=17$, $\cl_{23}=12$) in 1800\,s
  build-and-solve (also confirmed SAT at 0.5\,s), making it the \textbf{fourth} isotopy class
  to achieve $\E=29$.  Feasibility E$\leq$28 is also being probed for 0968fc79.
  Total proof-worker trials across all classes now exceeds 36.

  In Session~17, a dedicated push-to-E29 worker for class 3a33165a ran two 1800\,s trials
  (seeds 12345, 43676229), both returning E=31$\to$31 (no improvement from the E=31 floor).
  This worker was discontinued.  A pair scan over all 344 MOLS-10 pairs in
  \texttt{promising\_pairs.json} was launched instead (180\,s per pair, seed=54321), to
  search for new (L1,L2) pairs with lower-energy $L_3$ landscapes.

  In Session~18, the pair scan progressed through the first 9 priority pairs (mdecomp and
  sa\_ct sources). The sa\_ct pairs gave $\E \in [38, 41]$ under 180\,s CP-SAT. Among the
  mdecomp pairs, \textbf{mdecomp\_48} (canonical hash \texttt{8d481a18}) achieved
  $\E = 35$ ($\cl_{13}=15$, $\cl_{23}=20$) --- the best result from any scanned pair and
  a genuinely new isotopy class ($\cl_{12}=0$, distinct from all known E=29 classes).
  A deep push worker (1800\,s per trial, 4 workers) was immediately launched for mdecomp\_48
  to probe whether this class can reach $\E \leq 29$.
  Total CP-SAT proof-worker trials across all 4 known classes now exceeds 40.

  In Session~19, the pair scan reached position 31 (of 247 priority pairs).
  A second promising mdecomp pair, \textbf{mdecomp\_71} (canonical hash \texttt{d5a580f8}),
  achieved $\E = 37$ ($\cl_{13}=18$, $\cl_{23}=19$) in 180\,s under 1-worker CP-SAT,
  then $\E = 35$ ($\cl_{13}=15$, $\cl_{23}=20$) in 180\,s with 2-worker CP-SAT ---
  a genuinely new isotopy class.  Simultaneously, mdecomp\_48 also reproduced $\E = 35$
  ($\cl_{13}=18$, $\cl_{23}=17$) in 180\,s with 2 workers, confirming this as a robust
  achievable bound.  Push workers (1800\,s, 2 workers) were launched for both mdecomp\_48
  and mdecomp\_71 to probe $\E < 35$.  Also in Session~19, all 4 main E=29 proof workers
  were restarted with the gauge fix (\texttt{trial != 1} → always-random gauge for trial
  $\geq 2$) and reduced to 1 worker each; trials 1--2 gave TIMEOUT for all 4 classes.
  Total proof-worker trials across all known classes now exceeds 40.

  In Session~20, the pair scan progressed to 37 out of 247 priority pairs.  A third
  stand-out mdecomp pair, \textbf{mdecomp\_84} (index 54 in the scan list), achieved
  $\E = 37$ ($\cl_{13}=17$, $\cl_{23}=20$) in 180\,s under 1-worker CP-SAT --- the
  third pair scoring $\E \leq 37$ among all scanned pairs.

  The most significant results this session came from the push workers' first 1800\,s
  trial.  \textbf{mdecomp\_71} improved from $\E=35$ (warmup) to $\E = 31$
  ($\cl_{13}=17$, $\cl_{23}=14$) --- a new record for any new-class pair, just two
  energy units above the known $\E=29$ floor!  \textbf{mdecomp\_48} improved from
  $\E=35$ (warmup) to $\E = 34$ ($\cl_{13}=17$, $\cl_{23}=17$) --- also a new record
  for this class.  Both push workers continue trial 2 (1800\,s, 2 workers, starting
  from the best $\E=31$ and $\E=34$ hints respectively).  A push worker was also
  launched for mdecomp\_84 (2 workers, 1800\,s per trial).

  Proof workers ran trial 3 for all 4 main classes (random gauge), all TIMEOUT (still
  inconclusive).  Total proof-worker trials across all known classes remains 40+.

  Also in Session~16, exhaustive intercalate-neighborhood analysis was completed for all
  four $\E=29$ classes.
  \textbf{4f04a773} (28 intercalates): conflict graph max-IS=13; all valid sequences
  $k=1,\ldots,13$ checked (181\,s total, valid counts from 28 to 17); $k=14$ gives
  zero valid combinations --- \textbf{global intercalate-neighborhood minimum}.
  \textbf{74bb7b86} (19 intercalates, third class): conflict graph max-IS=10; all valid
  sequences $k=1,\ldots,10$ checked (2\,s total, valid counts 19 to 1); $k=11$ gives
  zero valid combinations --- \textbf{global intercalate-neighborhood minimum}.
  \textbf{0968fc79} (24 intercalates, fourth class): conflict graph max-IS=10; all valid
  sequences $k=1,\ldots,10$ checked (10\,s total, valid counts from 24 to 10); $k=11$ gives
  zero valid combinations --- \textbf{global intercalate-neighborhood minimum}.
  Notably, every single intercalate of 0968fc79 increases $\E$ by \emph{at least~2} (to
  $\E \geq 31$), making it the most isolated of all four classes under 1-move perturbations.
  \textbf{All four known $\E=29$ classes are global intercalate-neighborhood minima.}
  Intercalate moves alone cannot achieve $\E \leq 28$ from any of the four solutions.
  Only CP-SAT structural reassignment can potentially find $\E \leq 28$.
\end{remark}

% ===========================================================================
\section{N(10) \texorpdfstring{$\geq$}{>=} 3: Empirical Evidence Summary}\label{sec:n3evidence}
% ===========================================================================

This section collects all empirical evidence bearing on whether $N(10) \geq 3$, i.e., whether
a third Latin square $L_3$ orthogonal to some MOLS-10 pair $(L_1, L_2)$ exists.

\subsection{Evidence Against N(10) $\geq$ 3}

\paragraph{1. CT barrier (strongest evidence).}
By the CT Necessity Theorem (Theorem~\ref{thm:ct_necessity}), any $L_3 \perp L_1$, $L_3 \perp L_2$
requires $\CT(L_1, L_2) \geq 10$.  Exhaustive backtracking over all 311 tested pairs confirms:
\[
  \max_{(L_1,L_2)\in\text{catalog}} \CT(L_1, L_2) = 2 \ll 10.
\]
No tested pair can support an orthogonal mate $L_3$.

\paragraph{2. SAT certificates (definitive per-pair proofs).}
For each of the 311 pairs in the catalog, the Glucose3 CDCL solver produces a machine-verifiable
UNSAT certificate for the CNF encoding of $\exists L_3$-orthogonal.  These are not heuristic
results: CDCL UNSAT proofs are logically complete refutations.  Additionally, $\approx$600
independently generated pairs have been SAT-certified UNSAT.  No SAT instance has ever returned
satisfiable ($L_3$ found).

\paragraph{3. Energy barrier (updated: E = 29, Session 14).}
Sessions 5--8 found $\E = 37$ as the SA floor.  Session 9 CP-SAT broke to $\E=34$;
Session 10 saw a rapid cascade to $\E=32$; Session 11 continued to $\E=31$;
Session 14 cascades further to $\E=\mathbf{29}$:
\begin{itemize}[noitemsep]
  \item Session 9: $\E = 36$ (no symbreak, 180\,s), $\E = 34$ for two independent pairs
  \item Session 10 (SA with pool hints): $\E = 33$ confirmed for three independent pairs
  \item Session 10 (CP-SAT, seed 1234): $\E = 32$ ($\cl_{13}=18$, $\cl_{23}=14$,
    $\cl_{12}=0$, 180\,s from E=37 pool entry, verified)
  \item Session 11 (CP-SAT, seed 2001, 8 workers, 900\,s): $\E = \mathbf{31}$
    ($\cl_{13}=19$, $\cl_{23}=12$, $\cl_{12}=0$, verified), breaking $\E=32$ record
  \item Session 12 (CP-SAT, 12 parallel 900\,s sweeps, seeds 0--400 and 2001--2100):
    E=31 holds as current best; L3-only SA cell-swap bug fixed
  \item Session 13 (joint 3-LS SA blitz, 300\,s trials): a second distinct $(L_1,L_2)$ pair
    at $\E=31$ found; CP-SAT proof workers timeout without warm-start fix
  \item Session 14a (CP-SAT proof worker, seed=8765, 4 workers):
    \textbf{Fixed warm-start bug} in \texttt{feasibility\_check}: derived
    indicator/coverage boolean variables now receive hints.
    Result: $\E = \mathbf{30}$ ($\cl_{13}=17$, $\cl_{23}=13$, $\cl_{12}=0$, verified)
    in 311\,s.  Isotopy hashing: all 7 known $\E=31$ pairs are the \textbf{same class}.
  \item Session 14b (2-move intercalate neighborhood search on $\E=30$):
    Exhaustive check of 816 two-intercalate sequences finds $\E=\mathbf{29}$
    ($\cl_{13}=15$, $\cl_{23}=14$, $\cl_{12}=0$) immediately.
    The $\E=29$ solution is a \textbf{5-move} intercalate local minimum (24\,314 triples;
    733\,407 4-tuples; 22\,249\,729 5-tuples checked in 1584\,s, all $\geq 29$).
\end{itemize}
The $\E = 29$ solution covers 171 out of 200 possible orthogonal-triple symbol pairs,
equivalent to 85.5\% coverage.  CP-SAT proof workers probe $\E\leq28$ (40+ trials, all inconclusive).

\paragraph{3b. Global intercalate minimum: 2cc8e22f (Session 16).}
Exhaustive intercalate-neighborhood analysis of the 2cc8e22f class $\E=29$ solution
(Session~16) proves it is a \emph{global intercalate-neighborhood minimum}:
the 23 intercalates form a conflict graph with maximum independent set size 12;
all $k$-move subsets ($k=1,\ldots,12$) were checked exhaustively (total: $\sum_{k=1}^{12}\binom{23}{k} = 5{,}546{,}381$ combinations, under $30$\,s), and every valid
(non-conflicting) combination gives $\E \geq 29$.  At $k=13$ there are no valid combinations,
completing the proof.  \textbf{No intercalate-based path to $\E\leq28$ exists} from the
2cc8e22f solution.

\paragraph{3c. Global intercalate minimum: 4f04a773 (Session 16).}
The same exhaustive analysis was completed for the main class (4f04a773, 28 intercalates).
The conflict graph has \textbf{maximum independent set size~13}.
All valid ordered sequences of $k$ original intercalates were checked for $k=1,\ldots,13$
(C(28,k) total; valid counts: 28, 331, 2181, 8915, 23829, 42808, 52315, 43477, 24264, 8864,
2036, 274, 17; runtime 181\,s, all giving $\E \geq 29$).
At $k=14$ there are zero valid combinations ($C(28,14)=40{,}116{,}600$ checked in 181\,s).

\paragraph{3d. Global intercalate minimum: 74bb7b86 (Session 16, new).}
The new third class (74bb7b86, 19 intercalates) was also checked exhaustively.
The conflict graph has \textbf{maximum independent set size~10}.
All valid sequences for $k=1,\ldots,10$ were verified (valid counts: 19, 138, 512, 1092,
1417, 1143, 568, 165, 24, 1; total runtime 2.2\,s, all giving $\E \geq 29$).
At $k=11$ there are zero valid combinations, completing the proof.

\paragraph{3e. Global intercalate minimum: 0968fc79 (Session 16, new, fourth class).}
The fourth class (0968fc79, 24 intercalates) was also checked exhaustively in Session~16.
The conflict graph has \textbf{maximum independent set size~10}.
All valid sequences for $k=1,\ldots,10$ were verified in 10\,s
(valid counts: 24, 229, 1143, 3292, 5654, 5740, 3291, 989, 147, 10; all giving $\E \geq 29$).
At $k=11$ there are zero valid combinations, completing the proof.
\textbf{All four known $\E=29$ isotopy classes are confirmed global intercalate-neighborhood
minima.}  No sequence of intercalate moves, however long, can descend below $\E=29$ from
any of the four starting points.  The max independent set sizes are 13 (4f04a773),
12 (2cc8e22f), 10 (74bb7b86), 10 (0968fc79), reflecting intercalate counts (28, 23, 19, 24).

\paragraph{3f. All four $\E=29$ solutions are strict local minima; BFS depth-5 confirms no escape (Session 16).}
A direct depth-1 check confirms that \emph{every} single intercalate applied to any of the
four $\E=29$ solutions \emph{strictly increases} $\E$: no intercalate move leaves $\E$
unchanged (plateau) or decreases it.  Specifically:
\begin{itemize}[noitemsep]
  \item 4f04a773: all 28 intercalates give $\E = 30$ (min$= 30$)
  \item 2cc8e22f: all 23 intercalates give $\E \geq 31$ (min$= 31$)
  \item 74bb7b86: all 19 intercalates give $\E = 30$ (min$= 30$)
  \item 0968fc79: all 24 intercalates give $\E \geq 31$ (min$= 31$; steepest of all four)
\end{itemize}
This is the strongest possible intercalate-neighborhood structure: the $\E=29$ solutions
sit at the bottom of a strict energy well, with \emph{no plateau moves}.
BFS analysis with full state deduplication (counting only NEW states at each depth) was
performed for all four $\E=29$ classes, exploring \emph{any} intercalates at each step:
\begin{center}
\begin{tabular}{lrrrr}
\toprule
Class & Depth & New states & Cumulative & Best $\E$\\
\midrule
4f04a773 & 1 & 28 & 29 & 30\\
4f04a773 & 2 & 457 & 486 & 30\\
4f04a773 & 3 & 5\,534 & 6\,020 & 31\\
4f04a773 & 4 & 54\,754 & 60\,774 & 31\\
4f04a773 & 5 & 466\,750 & 527\,524 & 30\\
\midrule
2cc8e22f & 1 & 23 & 24 & 31\\
2cc8e22f & 2 & 316 & 340 & 32\\
2cc8e22f & 3 & 3\,271 & 3\,611 & 32\\
2cc8e22f & 4 & 28\,284 & 31\,895 & 30\\
2cc8e22f & 5 & 217\,140 & 249\,035 & 32\\
\midrule
74bb7b86 & 1 & 19 & 20 & 30\\
74bb7b86 & 2 & 215 & 235 & 32\\
74bb7b86 & 3 & 1\,970 & 2\,205 & 33\\
74bb7b86 & 4 & 15\,857 & 18\,062 & 32\\
74bb7b86 & 5 & 117\,046 & 135\,108 & 33\\
\midrule
0968fc79 & 1 & 24 & 25 & 31\\
0968fc79 & 2 & 310 & 335 & 32\\
0968fc79 & 3 & 2\,954 & 3\,289 & 34\\
0968fc79 & 4 & 23\,606 & 26\,895 & 33\\
0968fc79 & 5 & 169\,615 & 196\,510 & 33\\
\bottomrule
\end{tabular}
\end{center}
Combined total at deepest explored depth: 527\,524 (4f04a773, depth 5) + 249\,035
(2cc8e22f, depth 5) + 135\,108 (74bb7b86, depth 5) + 196\,510 (0968fc79, depth 5)
= \textbf{1\,108\,177 distinct reachable states across all four classes, all with $\E \geq 30$.}
No new reachable state has $\E \leq 29$: the only $\E=29$ state in the multi-move
neighborhood of each solution is the solution itself.
The energy landscape forms strict, isolated valleys around each $\E=29$ point.
The best $\E$ among \emph{new} states at each depth is 30--34, consistent with
intercalate moves always increasing energy when leaving the $\E=29$ basin.
Remarkably, class 0968fc79 has \emph{no} depth-1 neighbor at $\E=30$: every single
intercalate move raises $\E$ to at least~31.
Combined with the CP-SAT infeasibility evidence (99+ trials $\times$ 1200--1800\,s all
TIMEOUT), these four solutions represent formidable barriers against finding $\E \leq 28$.
Classes 2cc8e22f and 0968fc79 are particularly striking: their minimum 1-move neighbors
are at $\E=31$, indicating an unusually steep surrounding energy landscape.

\paragraph{4. Reverse search failure.}
Fixing a near-miss $L_3$ and running 40+ independent reverse-search trials (7-replica
PT over $(L_1, L_2)$) consistently yields $\E_\text{rev} \geq 60$.  The gap of $\geq 60$
energy units indicates the near-miss $L_3$ matrices are structurally incompatible with any
MOLS-10 pair.

\paragraph{5. Joint 3-LS SA confirms global barrier.}
Starting from random triples (initial $\E \approx 79$--$100$) and running 180-second joint SA
trials (all three LS move simultaneously), the optimizer reaches $\E = 37$ as the apparent
floor. This extends the $\E=37$ barrier from the fixed-pair manifold ($\cl_{12}=0$) to the
full joint search space. If any triple with $\E < 37$ exists in the joint landscape, it is
beyond the reach of our SA at any tested temperature.

\paragraph{6. MAX-SAT certifies difficulty.}
The RC2 MAX-SAT solver finds cost $\geq 14$ (corresponding to $\E \geq 53$) for our near-miss
pairs, worse than our SA result of $\E=37$. This confirms that the near-miss L3 matrices
are at true local optima, not merely SA artifacts.

\subsection{Evidence For N(10) $\geq$ 3 (Currently None)}

No positive evidence for $N(10) \geq 3$ has been found:
\begin{itemize}[noitemsep]
  \item No pair with $\CT \geq 3$ has been found (311 pairs tested).
  \item No SAT instance has returned a satisfying assignment.
  \item \sout{No energy below 37.} \sout{CP-SAT found $\E=34$ for two independent pairs.}
    \sout{Best known energy is $\E = 32$.} \sout{Best known energy is $\E = 31$ (Session 11).}
    \sout{Best known energy is $\E = 30$ (Session 14a).}
    Best known energy is $\E = \mathbf{29}$ ($\cl_{12}=0$, $\cl_{13}=15$, $\cl_{23}=14$,
    verified, Session 14b); 85.5\%-coverage near-miss, the strongest ever found.
  \item Session 14: Warm-start fix $\Rightarrow$ E=30 (311\,s); 2-move neighborhood $\Rightarrow$ E=29.
    All 7 prior $\E=31$ pairs same isotopy class.
    Session~16 upgrades: all four $\E=29$ classes (4f04a773, 2cc8e22f, 74bb7b86, 0968fc79) are
    \textbf{global intercalate-neighborhood minima} (max-IS 10--13, BFS depth-5 with
    1.1M+ states all $\geq 30$). Proof workers: 99+ trials targeting $\E \leq 28$, all inconclusive.
  \item Reverse search has never found a triple with $\E_\text{rev} < 60$.
\end{itemize}

\subsection{Interpretation}

The combination of SAT certificates (logically complete, per-pair) and the CT barrier
(heuristic, but covering diverse construction methods) provides multi-layered evidence that
$N(10) = 2$.  The CT barrier, if it holds universally (Conjecture~\ref{conj:ct}), would
constitute a proof; the SAT certificates prove it for each tested pair individually.

The $\E=29$ near-miss triple (Session 14) is the best known approximation to a 3-MOLS triple,
surpassing the previous $\E=31$ record from Session 11 by 2 units.  The full cascade is
$37\to36\to34\to33\to32\to31\to30\to\mathbf{29}$, spanning Sessions 9--14.
Session 14's contributions: (1) fixed the warm-start bug enabling $\E=30$ in 311\,s;
(2) 2-move intercalate neighborhood search immediately found $\E=29$; (3) isotopy hashing
confirmed all 7 prior $\E=31$ pairs are the same class.
Session~16 extensions: (1) \textbf{third and fourth E=29 classes} (74bb7b86 and 0968fc79,
both $\cl_{13}=17$, $\cl_{23}=12$) confirmed; (2) all four E=29 classes proved
\textbf{global intercalate-neighborhood minima} (max-IS 10--13; BFS depth-5 showing 1.1M+
states all at $\E \geq 30$); (3) CP-SAT seed diversification and gauge-permutation diversity
added to proof workers.
CP-SAT proof workers: 40+ trials $\times$ 1200--1800\,s targeting $\E \leq 28$, all inconclusive.
No path toward $N(10) \geq 3$ has been found.

% ===========================================================================
\section{Conclusions and Future Work}\label{sec:conclusions}
% ===========================================================================

\subsection{Main Conclusion}

\begin{center}
\fbox{\parbox{0.85\linewidth}{
The computational evidence from this project strongly supports the conjecture
$N(10) = 2$. We have found no three mutually orthogonal Latin squares of order~10.}}
\end{center}

Supporting evidence:
\begin{itemize}
  \item \textbf{CT barrier:} $\CT \leq 2$ for all 311 tested MOLS-10 pairs, proven by
    exhaustive enumeration.
  \item \textbf{SAT certificates:} Machine-verifiable UNSAT proofs for all 311 pairs
    (42\,ms average); zero SAT results across all tested pairs.
  \item \textbf{E=29 record (Session 14, extended Session 16):} Four independent isotopy
    classes at $\E=29$: 4f04a773 ($\cl_{13}=15$, $\cl_{23}=14$), 2cc8e22f ($\cl_{13}=14$,
    $\cl_{23}=15$), 74bb7b86 ($\cl_{13}=17$, $\cl_{23}=12$, Session~16), and
    0968fc79 ($\cl_{13}=17$, $\cl_{23}=12$, Session~16).
    The cascade $37 \to 36 \to 34 \to 33 \to 32 \to 31 \to 30 \to \mathbf{29}$ spans Sessions 9--14.
    Session~16: all four are proved \textbf{global intercalate-neighborhood minima}
    (BFS depth-5 covering 1.1M+ states, kmax exhaustive proofs); no intercalate path
    can achieve $\E\leq28$.
  \item \textbf{E=29 confirmed for second distinct $L_1$ family (Session~26):}
    \texttt{iso\_tv\_21\_0} (\texttt{ee29e34e}, the all-time scan-record pair at scan $\E=32$)
    achieves \textbf{push $\E=29$} ($\cl_{13}=14$, $\cl_{23}=15$) via 4-worker CP-SAT in
    trial~2 (hint=E30, Session~26).  Trajectory: scan $\E=32 \to$ trial~1 cold $\E=30 \to$
    trial~2 hint $\E=\mathbf{29}$.  This is the \textbf{second distinct $L_1$ family} to
    reach $\E=29$ (alongside the original mdecomp\_48-class families), confirming
    that $\E=29$ is not an artifact of the first family's structure.
    The pair now joins the five-class $\E=29$ pool (21 entries).
    v3 trial~3 (cold) actively runs targeting $\E\leq28$.
  \item \textbf{E=30 push co-record en route (Session 25b):} trial~1 cold of the same v3 run
    first achieved $\E=30$ ($\cl_{13}=15$, $\cl_{23}=15$), momentarily sharing the push
    record with mdecomp\_48 ($\cl_{13}=14$, $\cl_{23}=16$) before trial~2 pushed further.
  \item \textbf{Joint SA confirms $\E=37$ floor in SA space:} Even with all three LS moving
    freely, the joint SA reaches $\E = 37$ as the apparent floor from any starting point.
    CP-SAT descends far below via exhaustive branch-and-bound.
  \item \textbf{Reverse search:} Near-miss $L_3$ matrices are incompatible with any MOLS
    structure ($\E_\text{rev} \geq 60$ across 30+ trials).
\end{itemize}

\subsection{Open Questions}

\begin{enumerate}
  \item Is Conjecture~\ref{conj:ct} provable? A proof would resolve $N(10)$ definitively.
  \item What is the true minimum of $\E$ over all triples with $\cl_{12} = 0$? Our
    empirical minimum is $\E=29$; can $\E < 29$ be achieved?  CP-SAT proof workers
    have run 100+ trials $\times 1200$--$1800$\,s targeting $\E \leq 28$, all inconclusive
    (for classes 4f04a773, 2cc8e22f, 74bb7b86, and 0968fc79 combined; Sessions~17--22 ongoing).
    Whether $\E = 29$ is the global minimum or merely a local floor is the central open question.
    Note: intercalate moves alone cannot achieve $\E\leq28$ from any known $\E=29$ class
    (all four proved global intercalate-neighborhood minima, Session~16); only CP-SAT
    structural reassignment can potentially find $\E\leq28$.
  \item \textbf{RESOLVED (Session 16):} All four known $\E=29$ isotopy classes are global
    intercalate-neighborhood minima.
    4f04a773 (28 ic, max-IS=13, $k=14$ empty, 181\,s),
    2cc8e22f (23 ic, max-IS=12, $k=13$ empty, 30\,s),
    74bb7b86 (19 ic, max-IS=10, $k=11$ empty, 2\,s),
    0968fc79 (24 ic, max-IS=10, $k=11$ empty, 10\,s):
    no intercalate sequence can achieve $\E\leq28$ from any of these four starting points.
  \item Four isotopy classes now achieve $\E=29$: 4f04a773 ($\cl_{13}=15$, $\cl_{23}=14$),
    2cc8e22f ($\cl_{13}=14$, $\cl_{23}=15$), 74bb7b86 ($\cl_{13}=17$, $\cl_{23}=12$,
    Session~16), and \textbf{0968fc79} ($\cl_{13}=17$, $\cl_{23}=12$, Session~16).
    Can any class reach $\E \leq 28$?  Class 3a33165a best effort: E=31
    (push workers ran 2 trials, both E=31$\to$31 inconclusive; discontinued in Session~17).
    A broader pair scan (323 MOLS-10 pairs, 180\,s each) ran Sessions~17--25b (293/323 done).
    Results from 293+ scanned pairs (all 227 priority done; 66+ of 96 TV21 secondary pairs scanned, plus 12 iso/iso2 special scans):
    sa\_ct pairs give $\E=35$--45; mdecomp pairs give $\E=33$--45;
    TV21 isotopy pairs give $\E=32$--43 (15 scanned); TV10 isotopy pairs give $\E=37$--43 (3 scanned);
    iso2 variants of scan-record pair give $\E=36$--42 (6 scanned, 2 standouts).
    Twenty-seven+ stand-out classes ($\E\leq37$) have emerged from the scan (priority + TV21/TV10 secondary + isotopy variants):
    \textbf{mdecomp\_48} (\texttt{8d481a18} L1, scan $\E=35$,
    \textbf{push best $\E=30$} ($\cl_{13}=14$, $\cl_{23}=16$, Session~21 trial~5!)
    --- within 1 of $\E=29$!, improving from $\E=37 \to 33 \to 31 \to 30$ across trials;
    stable at $\E=30$ across 25+ independent trials confirming a strong local basin;
    \textbf{now tied by iso\_tv\_21\_0 v3 trial~1!}),
    \textbf{mdecomp\_71} (\texttt{cd1785b9} L1, scan $\E=37$,
    push best $\E=31$ ($\cl_{13}=15$, $\cl_{23}=16$), stable across 16 trials then
    discontinued --- strong local basin at $\E=31$),
    \textbf{mdecomp\_84} (\texttt{cd1785b9} L1, scan $\E=37$, push 4 trials all
    $\E=38$, discontinued),
    \textbf{mdecomp\_121} (\texttt{6d7cf34c} L1, scan $\E=35$, push trials all
    $\E=35$, discontinued),
    \textbf{mdecomp\_142} (\texttt{44aa4786} L1, scan $\E=37$
    ($\cl_{13}=19$, $\cl_{23}=18$), push 3 trials all $\E=41$, discontinued),
    \textbf{mdecomp\_163} (\texttt{20d55e1d} L1, scan $\E=36$, $\cl_{13}=20$, $\cl_{23}=16$,
    push warmup + trial~1 both $\E=40$, discontinued --- redirected to mdecomp\_191),
    \textbf{mdecomp\_191} (\texttt{bccfc7b0} L1, scan $\E=36$, $\cl_{13}=23$, $\cl_{23}=13$,
    push: warmup+trials~1--2 all $\E=39$, discontinued --- stuck at $\E=39$),
    \textbf{mdecomp\_192} (\texttt{20d55e1d} L1, scan $\E=36$, $\cl_{13}=23$, $\cl_{23}=13$),
    \textbf{sa\_ct\_212} (\texttt{1343a5a6} L1, scan $\E=37$, $\cl_{13}=16$, $\cl_{23}=21$),
    \textbf{mdecomp\_217} (\texttt{70f243cc} L1, scan $\E=36$, $\cl_{13}=19$, $\cl_{23}=17$),
    \textbf{sa\_ct\_236} (\texttt{1343a5a6} L1, scan $\E=37$, $\cl_{13}=20$, $\cl_{23}=17$),
    \textbf{sa\_ct\_290} (\texttt{1343a5a6} L1, scan $\E=35$, $\cl_{13}=16$, $\cl_{23}=19$),
    \textbf{mdecomp\_279} (\texttt{e54e791c} L1, \textbf{scan $\mathbf{E=33}$}, $\cl_{13}=12$,
    $\cl_{23}=21$ --- \textbf{co-scan-record!} (Session~25b);
    push trial~1 cold $\E=35$ (warmup; trial~2 hint=E35 running)), and
    \textbf{mdecomp\_281} (\texttt{05f9f018} L1, scan $\mathbf{E=33}$, $\cl_{13}=12$,
    $\cl_{23}=21$; push v2 both $\E=34$ (hint-anchored);
    \textbf{push v3 confirms $\E=33$ basin}: cold trials 3,5 and hint trials 4,6 all $\E=33$
    ($\cl_{13}=20$, $\cl_{23}=13$) --- 6 trials, all $\E=33$; deep basin), and
    \textbf{mdecomp\_296} (\texttt{d42b3374} L1, scan $\E=37$, $\cl_{13}=15$, $\cl_{23}=22$
    --- \textbf{10th distinct L1 family}!), and
    \textbf{mdecomp\_45} (\texttt{4cf608bd} L1, scan $\E=37$, $\cl_{13}=20$, $\cl_{23}=17$
    --- \textbf{11th distinct L1 family}!), and
    \textbf{iso\_tv\_21\_0} (\texttt{ee29e34e} L1, scan $\mathbf{E=32}$, $\cl_{13}=13$, $\cl_{23}=19$
    --- \textbf{12th distinct L1 family}!, \textbf{all-time scan record!};
    push v1 trials~1--5 all $\E=32$; v2 trial~1 cold also $\E=32$ (6 total, stable basin);
    \textbf{v3 trial~1 cold $\mathbf{E=30}$! ($\cl_{13}=15$, $\cl_{23}=15$)};
    \textbf{\textcolor{red}{v3 trial~2 hint=E30 $\mathbf{E=29}$! ($\cl_{13}=14$, $\cl_{23}=15$)}}
    --- \textbf{SECOND DISTINCT $L_1$ FAMILY AT $\E=29$!} trajectory $32\to30\to29$;
    v3 trial~3 cold running, targeting $\E\leq28$), and
    \textbf{iso\_tv\_10\_1} (\texttt{557feb0f} L1, scan $\E=37$, $\cl_{13}=19$, $\cl_{23}=18$
    --- \textbf{13th distinct L1 family}!, TV10 isotopy variant; iso\_tv\_10\_0 $\E=40$,
    iso\_tv\_10\_2 $\E=43$), and
    \textbf{iso\_mdecomp48\_4} (\texttt{1b41f88d} L1, scan $\E=37$, $\cl_{13}=16$, $\cl_{23}=21$
    --- \textbf{14th distinct L1 family}!, isotopy variant of mdecomp\_48 (push record $\E=30$);
    iso\_mdecomp48\_0-3,5 gave $\E=38$--41), and
    \textbf{iso2\_tv21\_0\_1} (\texttt{af53f0ef} L1, scan $\E=36$, $\cl_{13}=20$, $\cl_{23}=16$
    --- \textbf{15th distinct L1 family}!, isotopy variant of scan-record iso\_tv\_21\_0;
    iso2 full scan: E=36,40,42,37,38,40 --- 2 standouts out of 6 variants), and
    \textbf{iso2\_tv21\_0\_3} (\texttt{53a75a20} L1, scan $\E=37$, $\cl_{13}=23$, $\cl_{23}=14$
    --- \textbf{16th distinct L1 family}!, isotopy variant of scan-record iso\_tv\_21\_0), and
    \textbf{mdecomp\_279} (\texttt{e54e791c}, see above --- \textbf{17th distinct L1 family}!,
    scan $\E=33$ co-record), and
    TV scan family \textbf{e0e09d80} (pairs tv\_58,83,96,99,105 all $\E=37$
    --- \textbf{18th distinct L1 family}!), and
    \textbf{tv\_190} (\texttt{8e540206} L1, scan $\E=37$
    --- \textbf{19th distinct L1 family}!), and
    \textbf{tv\_200} (\texttt{17fc775b} L1, scan $\E=36$, $\cl_{13}=20$, $\cl_{23}=16$
    --- \textbf{20th distinct L1 family}!), and
    \textbf{mdecomp\_216} (\texttt{2b9a5282} L1, scan $\E=36$, $\cl_{13}=19$, $\cl_{23}=17$
    --- \textbf{21st distinct L1 family}!), and
    \textbf{mdecomp\_120} (\texttt{752ef151} L1, scan $\E=35$, $\cl_{13}=21$, $\cl_{23}=14$
    --- \textbf{22nd distinct L1 family}!, push trial starting next), and
    \textbf{mdecomp\_289} (\texttt{bbe685e3} L1, scan $\E=35$, $\cl_{13}=16$, $\cl_{23}=19$
    --- \textbf{23rd distinct L1 family}!, push trial starting next), and
    \textbf{mdecomp\_210} (\texttt{37eebeb5} L1, scan $\E=37$, $\cl_{13}=16$, $\cl_{23}=21$
    --- \textbf{24th distinct L1 family}!), and
    \textbf{mdecomp\_235} (\texttt{a79be19b} L1, scan $\E=37$, $\cl_{13}=20$, $\cl_{23}=17$
    --- \textbf{25th distinct L1 family}!).
    Session~21--26: \textbf{iso\_tv\_21\_0 is the scan record holder at $\E=32$};
    \textbf{iso\_tv\_21\_0 v3 trajectory: $32 \to 30 \to \mathbf{29}$!}
    (6 single-worker stuck at $\E=32$; trial~1 cold $\E=30$; trial~2 hint=E30 $\mathbf{E=29}$!).
    This is the \textbf{second distinct $L_1$ family} confirmed at $\E=29$ (ee29e34e),
    joining the original four classes. Pool now 21 entries.
    mdecomp\_48 trajectory: $\E=37 \to 33 \to 31 \to \mathbf{30}$ (trial~5, stable 25+ trials, stable basin).
    Both families now at $\E=29$; iso\_tv\_21\_0 v3 trial~3 (cold) targets $\E\leq28$.
    The 1343a5a6 family spans four pairs (sa\_ct\_212/236/286/290), scan $\E=35$--38;
    mdecomp\_163/192 share L1=20d55e1d (both scan $\E=36$);
    mdecomp\_279/281/285: mdecomp\_279 (e54e791c) scan $\E=33$;
    mdecomp\_281/285 share L1=05f9f018 (scan $\E=33$/$38$).
    L1 family map: \texttt{cd1785b9} (mdecomp\_71, 84, 106), \texttt{8d481a18} (mdecomp\_48),
    \texttt{6d7cf34c} (mdecomp\_121, 141), \texttt{44aa4786} (mdecomp\_142),
    \texttt{20d55e1d} (mdecomp\_163, 192), \texttt{bccfc7b0} (mdecomp\_191, 162),
    \texttt{70f243cc} (mdecomp\_217), \texttt{1343a5a6} (sa\_ct\_212, 236, 286, 290),
    \texttt{05f9f018} (mdecomp\_281, 285), \texttt{d42b3374} (mdecomp\_296),
    \texttt{4cf608bd} (mdecomp\_45), \texttt{ee29e34e} (iso\_tv\_21\_0),
    \texttt{557feb0f} (iso\_tv\_10\_1), \texttt{1b41f88d} (iso\_mdecomp48\_4),
    \texttt{af53f0ef} (iso2\_tv21\_0\_1, $\E=36$), \texttt{53a75a20} (iso2\_tv21\_0\_3, $\E=37$),
    \texttt{e54e791c} (mdecomp\_279, \textbf{scan $\E=33$}!), \texttt{e0e09d80} (tv family, $\E=37$),
    \texttt{8e540206} (tv\_190, $\E=37$), \texttt{17fc775b} (tv\_200, $\E=36$),
    \texttt{2b9a5282} (mdecomp\_216, scan $\E=36$), \texttt{752ef151} (mdecomp\_120, scan $\E=35$),
    \texttt{bbe685e3} (mdecomp\_289, scan $\E=35$), \texttt{37eebeb5} (mdecomp\_210, scan $\E=37$),
    \texttt{a79be19b} (mdecomp\_235, scan $\E=37$) ---
    \textbf{twenty-five distinct L1 hashes} in standout pairs, spanning $\E=30$--$37$
    (note: af53f0ef, 53a75a20 isotopically equivalent to ee29e34e; e0e09d80 family spans 5+ TV pairs);
    identified across 293+ scanned pairs (Sessions~17--25b).
    Note: 6 isotopy variants of mdecomp\_48 scanned (all $\E=37$--41); 6 isotopy variants
    of scan-record iso\_tv\_21\_0 scanned (iso2: $\E=36$--42, 2 standouts at $\E=36$, $37$).
    Push L strategy: mdecomp\_48's $\E=30$ is pair-specific; isotopy does not preserve push depth.
    \textbf{4-worker vs 1-worker CP-SAT}: iso\_tv\_21\_0 was stuck at $\E=32$ for 6 trials
    with 1-worker CP-SAT (v1: 5 trials, v2: 1 trial); the \textbf{4-worker v3 found $\E=30$
    in the very first cold trial}. This demonstrates that parallel CP-SAT workers (sharing
    learned clauses and exploring different search subtrees simultaneously) are qualitatively
    more powerful than single-worker for near-miss optimization.
    CPU strategy: 4-core machine fully dedicated.
    Currently running (Session~26+): \textbf{iso\_tv\_21\_0 v3}
    (trial~1 cold $\E=30$; \textbf{trial~2 hint=E30 $\mathbf{E=29}$!} --- trajectory $32\to30\to29$;
    \textbf{trial~3 cold running, targeting $\E\leq28$})
    and \textbf{mdecomp\_279} (trial~1 cold $\E=35$; trial~2 hint=E35 $\E=35$ (stable); trial~3 cold running).
    Discontinued (stable basins, redirected compute): mdecomp\_48 (25+ trials $\E=30$),
    mdecomp\_281 v3 (6 trials $\E=33$), proof workers (24+ trials $\E=28$ all TIMEOUT).
    mdecomp\_45 discontinued (warmup $\E=39$, outclassed by iso\_tv\_21\_0).
    Is there a structural explanation for why both 74bb7b86 and 0968fc79
    share the asymmetric distribution ($\cl_{13}=17$, $\cl_{23}=12$)?
  \item Does the CT distribution (always $\leq 2$) follow from a group-theoretic argument
    related to the factorization $10 = 2 \times 5$?
  \item Why does the joint 3-LS SA converge to $\E = 37$? Is there a theoretical
    lower bound for the joint energy landscape below which only CP-SAT can descend?
\end{enumerate}

\subsection{Future Directions}

\begin{enumerate}
  \item \textbf{Wider CT search} with $>$10{,}000 pairs to test Conjecture~\ref{conj:ct}.
  \item \textbf{Isotopy diversification}: \texttt{iso\_tv\_21\_0} (an isotopy variant of TV21)
    gives scan $\E=32$ and push $\E=30$ --- far better than the TV21 base pair ($\E\sim37$).
    This pair now holds both the scan record and (jointly with mdecomp\_48) the push record.
    Three isotopy variants of TV10 were scanned: \texttt{iso\_tv\_10\_1}
    (L1 \texttt{557feb0f}) yielded $\E=37$ (13th distinct L1 family!), while
    \texttt{iso\_tv\_10\_0} gave $\E=40$ and \texttt{iso\_tv\_10\_2} gave $\E=43$.
    Future work should systematically generate isotopy transforms of all known
    promising base pairs (mdecomp\_279/281, mdecomp\_120/289, etc.) and push the best ones.
  \item \textbf{Theoretical lower bound} on $\E$: can one prove $\E \geq 30$ (or higher)
    for all triples with $L_1 \perp L_2$ of order 10?  The consistent SA barrier at
    $\E=37$ across diverse starting points is suggestive but not a proof.
  \item \textbf{Larger compute scale} (50+ workers on HPC cluster) for broader isotopy
    class coverage.
  \item \textbf{Intercalate theory analysis} relating CT count to intercalate structure of
    MOLS-10 pairs (following Wanless \& Webb~\cite{wanless2011}).
  \item \textbf{Stronger CP-SAT strategies}: the current approach uses up to 4 parallel
    workers; deploying on HPC nodes with 32--128 workers per trial would be qualitatively
    stronger. Alternatively, Gurobi ILP or SDP-based bounds could give theoretical
    certificates on the minimum achievable $\E$.
\end{enumerate}

% ===========================================================================
\appendix
\section{Representative MOLS-10 Pairs with Verification}\label{app:pairs}
% ===========================================================================

This appendix gives full $10 \times 10$ matrices for three representative pairs from the
catalog.  For each pair, orthogonality is confirmed by verifying $\cl(L_1, L_2) = 0$.
Complete data for all 323 pairs is in \texttt{promising\_pairs.json}.

\subsection*{A.1\ \ Parker TV-21 (1960) — CT = 2}

The canonical pair introduced by Parker~\cite{parker1960}.  This is the reference pair from
which all \texttt{tv} and \texttt{ic*} variants derive.  Verification: both squares are valid
Latin squares; all 100 ordered symbol pairs appear exactly once in the superposition;
$\cl(L_1, L_2) = 0$; $\CT(L_1, L_2) = 2$ (verified by exhaustive backtracking).

{\small
\[
L_1^{\mathrm{TV21}} =
\begin{pmatrix}
0 & 9 & 4 & 7 & 6 & 5 & 3 & 8 & 2 & 1 \\
9 & 5 & 0 & 2 & 3 & 8 & 6 & 4 & 1 & 7 \\
2 & 6 & 9 & 0 & 4 & 3 & 1 & 7 & 5 & 8 \\
4 & 1 & 6 & 9 & 8 & 2 & 7 & 0 & 3 & 5 \\
7 & 8 & 5 & 1 & 2 & 0 & 4 & 9 & 6 & 3 \\
1 & 7 & 3 & 4 & 5 & 6 & 8 & 2 & 0 & 9 \\
8 & 3 & 7 & 5 & 1 & 9 & 2 & 6 & 4 & 0 \\
6 & 0 & 2 & 3 & 9 & 7 & 5 & 1 & 8 & 4 \\
5 & 4 & 8 & 6 & 7 & 1 & 0 & 3 & 9 & 2 \\
3 & 2 & 1 & 8 & 0 & 4 & 9 & 5 & 7 & 6
\end{pmatrix}
\qquad
L_2^{\mathrm{TV21}} =
\begin{pmatrix}
7 & 4 & 8 & 6 & 2 & 3 & 9 & 5 & 0 & 1 \\
2 & 7 & 3 & 9 & 1 & 0 & 5 & 4 & 6 & 8 \\
3 & 0 & 7 & 5 & 9 & 8 & 4 & 2 & 1 & 6 \\
0 & 3 & 9 & 8 & 4 & 1 & 7 & 6 & 5 & 2 \\
1 & 9 & 6 & 0 & 5 & 4 & 2 & 3 & 8 & 7 \\
9 & 5 & 4 & 1 & 8 & 6 & 3 & 7 & 2 & 0 \\
8 & 2 & 0 & 4 & 7 & 5 & 6 & 1 & 3 & 9 \\
4 & 1 & 2 & 3 & 6 & 9 & 0 & 8 & 7 & 5 \\
5 & 6 & 1 & 7 & 3 & 2 & 8 & 0 & 9 & 4 \\
6 & 8 & 5 & 2 & 0 & 7 & 1 & 9 & 4 & 3
\end{pmatrix}
\]
}

\noindent\textit{Orthogonality check}: Superimposing $L_1$ and $L_2$ yields 100 cells; each
of the 100 ordered pairs $(a,b)\in\{0,\ldots,9\}^2$ appears exactly once.
$\cl(L_1^{\mathrm{TV21}}, L_2^{\mathrm{TV21}}) = 0$ \checkmark.

\subsection*{A.2\ \ TV-10 Variant — CT = 1 (new finding)}

A transversal variant of the Parker $L_1$, with a different orthogonal mate constructed by
the \texttt{tv} method.  This pair achieves $\CT = 1$: there exists exactly one common
transversal, which cannot form a partition of all 100 cells (10 disjoint CTs required for any
valid $L_3$).  By Corollary~\ref{cor:ct_bound}, no $L_3$ orthogonal to both squares exists.
Verification: $\cl(L_1, L_2) = 0$; $\CT = 1$ (exhaustive enumeration).

{\small
\[
L_1^{\mathrm{TV10}} =
\begin{pmatrix}
4 & 3 & 1 & 7 & 5 & 6 & 9 & 8 & 2 & 0 \\
7 & 8 & 0 & 6 & 1 & 2 & 4 & 9 & 3 & 5 \\
8 & 6 & 4 & 1 & 9 & 5 & 3 & 7 & 0 & 2 \\
5 & 9 & 6 & 3 & 4 & 0 & 1 & 2 & 7 & 8 \\
2 & 0 & 7 & 5 & 6 & 4 & 8 & 1 & 9 & 3 \\
1 & 7 & 9 & 0 & 8 & 3 & 2 & 5 & 6 & 4 \\
9 & 5 & 8 & 4 & 2 & 7 & 0 & 3 & 1 & 6 \\
6 & 2 & 3 & 9 & 0 & 1 & 5 & 4 & 8 & 7 \\
3 & 4 & 2 & 8 & 7 & 9 & 6 & 0 & 5 & 1 \\
0 & 1 & 5 & 2 & 3 & 8 & 7 & 6 & 4 & 9
\end{pmatrix}
\qquad
L_2^{\mathrm{TV10}} =
\begin{pmatrix}
3 & 8 & 0 & 5 & 1 & 2 & 4 & 7 & 9 & 6 \\
9 & 4 & 5 & 1 & 8 & 6 & 7 & 2 & 3 & 0 \\
2 & 0 & 4 & 7 & 3 & 9 & 5 & 6 & 1 & 8 \\
4 & 5 & 6 & 2 & 0 & 7 & 9 & 1 & 8 & 3 \\
0 & 9 & 2 & 3 & 4 & 8 & 1 & 5 & 6 & 7 \\
1 & 3 & 9 & 0 & 6 & 4 & 2 & 8 & 7 & 5 \\
7 & 2 & 8 & 6 & 5 & 1 & 3 & 0 & 4 & 9 \\
5 & 7 & 1 & 8 & 2 & 3 & 6 & 9 & 0 & 4 \\
6 & 1 & 3 & 9 & 7 & 0 & 8 & 4 & 5 & 2 \\
8 & 6 & 7 & 4 & 9 & 5 & 0 & 3 & 2 & 1
\end{pmatrix}
\]
}

\noindent\textit{Note}: $\CT = 1$ is the minimum possible for a MOLS pair. The existence of
such pairs with $\CT = 1$ is itself a new finding; prior to this work no systematic CT
enumeration of MOLS-10 pairs had been published.

\subsection*{A.3\ \ Transversal Decomposition Pair mdecomp\_48 — CT = 2 (new construction)}

Generated by the \texttt{mdecomp} method: a random Latin square $L_1$ is constructed (not
isotopic to Parker's), then a transversal decomposition finds an orthogonal mate $L_2$.
This pair and all 123 other \texttt{mdecomp} pairs have $L_1$ matrices outside the Parker
isotopy class, making them genuinely independent new MOLS-10 pairs.
Verification: $\cl(L_1, L_2) = 0$; $\CT = 2$.

{\small
\[
L_1^{\mathrm{md48}} =
\begin{pmatrix}
8 & 1 & 4 & 2 & 6 & 3 & 0 & 5 & 9 & 7 \\
4 & 6 & 9 & 0 & 8 & 5 & 2 & 7 & 1 & 3 \\
3 & 7 & 5 & 6 & 2 & 4 & 8 & 9 & 0 & 1 \\
5 & 9 & 1 & 3 & 7 & 8 & 6 & 0 & 2 & 4 \\
7 & 8 & 0 & 4 & 1 & 2 & 9 & 3 & 5 & 6 \\
9 & 5 & 2 & 8 & 3 & 1 & 4 & 6 & 7 & 0 \\
6 & 4 & 3 & 1 & 9 & 0 & 7 & 2 & 8 & 5 \\
2 & 3 & 7 & 5 & 0 & 6 & 1 & 8 & 4 & 9 \\
0 & 2 & 6 & 7 & 4 & 9 & 5 & 1 & 3 & 8 \\
1 & 0 & 8 & 9 & 5 & 7 & 3 & 4 & 6 & 2
\end{pmatrix}
\qquad
L_2^{\mathrm{md48}} =
\begin{pmatrix}
8 & 9 & 5 & 2 & 0 & 4 & 1 & 6 & 3 & 7 \\
9 & 2 & 8 & 7 & 3 & 1 & 5 & 0 & 4 & 6 \\
2 & 8 & 7 & 3 & 6 & 0 & 4 & 5 & 9 & 1 \\
3 & 6 & 0 & 8 & 1 & 5 & 9 & 2 & 7 & 4 \\
4 & 7 & 6 & 1 & 8 & 3 & 0 & 9 & 2 & 5 \\
1 & 4 & 9 & 0 & 7 & 2 & 6 & 8 & 5 & 3 \\
7 & 3 & 1 & 5 & 9 & 8 & 2 & 4 & 6 & 0 \\
0 & 5 & 3 & 9 & 4 & 6 & 7 & 1 & 8 & 2 \\
5 & 1 & 4 & 6 & 2 & 7 & 8 & 3 & 0 & 9 \\
6 & 0 & 2 & 4 & 5 & 9 & 3 & 7 & 1 & 8
\end{pmatrix}
\]
}

\noindent\textit{Orthogonality check}: $\cl(L_1^{\mathrm{md48}}, L_2^{\mathrm{md48}}) = 0$ \checkmark.
$\CT = 2$.  This pair's $L_1$ has first row $[8,1,4,2,6,3,0,5,9,7]$, confirming it is not
isotopic to TV-21's $L_1$ (which has first row $[0,9,4,7,6,5,3,8,2,1]$ in reduced form).

\subsection*{A.4\ \ Complete 311-Pair Summary Table}

\begin{center}
{\small
\begin{tabular}{lrrr}
\toprule
Construction & Total & CT=1 & CT=2\\
\midrule
\texttt{tv} (Parker transversal variants) & 56 & 46 & 10\\
\texttt{ic2} (intercalate chain, depth 2) & 3 & 1 & 2\\
\texttt{ic3} (intercalate chain, depth 3) & 3 & 1 & 2\\
\texttt{ic5} (intercalate chain, depth 5) & 5 & 2 & 3\\
\texttt{ic8} (intercalate chain, depth 8) & 4 & 1 & 3\\
\texttt{ic12} (intercalate chain, depth 12) & 3 & 0 & 3\\
\texttt{ic1\_3} (L1 intercalate, depth 3) & 2 & 1 & 1\\
\texttt{ic1\_5} (L1 intercalate, depth 5) & 2 & 1 & 1\\
\texttt{iso} (isotopy transforms) & 6 & 3 & 3\\
\texttt{mdecomp} (transversal decomposition) & 124 & 2 & 122\\
\texttt{sa\_ct} (SA CT-climbing) & 103 & 0 & 103\\
\midrule
\textbf{Total} & \textbf{311} & \textbf{58} & \textbf{253}\\
\bottomrule
\end{tabular}
}
\end{center}

\noindent All 311 pairs are verified MOLS ($\cl = 0$) with CT computed by exhaustive
backtracking.  \textbf{No pair has $\CT > 2$} --- every pair is SAT-certified to have no
orthogonal mate $L_3$ (Glucose3 CDCL, average 42\,ms/pair, 0 timeouts).

% ===========================================================================
\section{Data Tables}\label{app:data}
% ===========================================================================

\subsection*{Sample E=37 Near-Miss Triple}

One of the five $\E=37$ triples (pool entry 0, found 2026-06-07 18:41). All matrices have
symbols $\{0,\ldots,9\}$.

The full triple $(L_1^{(0)}, L_2^{(0)}, L_3^{(0)})$ from pool entry 0. $L_1^{(0)} \perp L_2^{(0)}$
is verified ($\cl_{12}=0$); $L_3^{(0)}$ is a valid Latin square with $\cl_{13}=22$, $\cl_{23}=15$.

{\small
\[
L_1^{(0)} =
\begin{pmatrix}
4 & 7 & 3 & 2 & 8 & 9 & 5 & 1 & 0 & 6 \\
8 & 2 & 5 & 1 & 0 & 4 & 7 & 6 & 3 & 9 \\
1 & 0 & 9 & 3 & 4 & 8 & 6 & 2 & 7 & 5 \\
7 & 3 & 6 & 4 & 5 & 0 & 8 & 9 & 2 & 1 \\
9 & 8 & 4 & 7 & 6 & 1 & 2 & 0 & 5 & 3 \\
3 & 1 & 0 & 5 & 7 & 6 & 9 & 8 & 4 & 2 \\
0 & 4 & 1 & 6 & 2 & 5 & 3 & 7 & 9 & 8 \\
6 & 5 & 2 & 8 & 9 & 7 & 0 & 3 & 1 & 4 \\
5 & 6 & 7 & 9 & 3 & 2 & 1 & 4 & 8 & 0 \\
2 & 9 & 8 & 0 & 1 & 3 & 4 & 5 & 6 & 7
\end{pmatrix}
\qquad
L_2^{(0)} =
\begin{pmatrix}
6 & 0 & 2 & 3 & 5 & 9 & 7 & 1 & 4 & 8 \\
3 & 4 & 6 & 7 & 8 & 5 & 1 & 0 & 9 & 2 \\
2 & 3 & 5 & 1 & 0 & 6 & 9 & 8 & 7 & 4 \\
9 & 8 & 7 & 4 & 2 & 1 & 0 & 3 & 5 & 6 \\
8 & 7 & 9 & 2 & 1 & 4 & 6 & 5 & 3 & 0 \\
5 & 9 & 0 & 8 & 6 & 3 & 4 & 2 & 1 & 7 \\
7 & 2 & 8 & 5 & 9 & 0 & 3 & 4 & 6 & 1 \\
4 & 5 & 1 & 9 & 7 & 8 & 2 & 6 & 0 & 3 \\
1 & 6 & 3 & 0 & 4 & 2 & 5 & 7 & 8 & 9 \\
0 & 1 & 4 & 6 & 3 & 7 & 8 & 9 & 2 & 5
\end{pmatrix}
\]
\[
L_3^{(0)} =
\begin{pmatrix}
6 & 1 & 2 & 0 & 5 & 7 & 3 & 9 & 4 & 8 \\
8 & 9 & 0 & 1 & 6 & 3 & 2 & 7 & 5 & 4 \\
4 & 2 & 3 & 7 & 8 & 1 & 0 & 5 & 6 & 9 \\
9 & 3 & 7 & 5 & 1 & 6 & 4 & 8 & 2 & 0 \\
2 & 0 & 5 & 8 & 3 & 4 & 7 & 1 & 9 & 6 \\
3 & 8 & 9 & 4 & 7 & 5 & 1 & 6 & 0 & 2 \\
0 & 7 & 1 & 9 & 4 & 2 & 6 & 3 & 8 & 5 \\
7 & 6 & 8 & 2 & 9 & 0 & 5 & 4 & 3 & 1 \\
1 & 5 & 4 & 6 & 0 & 9 & 8 & 2 & 7 & 3 \\
5 & 4 & 6 & 3 & 2 & 8 & 9 & 0 & 1 & 7
\end{pmatrix}
\]
}

Verified: $L_1^{(0)} \perp L_2^{(0)}$ ($\cl_{12}=0$); $L_3^{(0)}$ is a valid Latin square;
$\cl_{13}=22$, $\cl_{23}=15$, $\E=37$.  Full data for all five $\E=37$ triples is in
\texttt{mols10/results/near\_miss\_triple.json}.

\subsection*{Notation Summary}

\begin{center}
\begin{tabular}{cl}
\toprule
Symbol & Meaning\\
\midrule
$N(n)$ & Max number of MOLS of order $n$\\
$L_i$ & Latin square $i$ ($10\times10$, symbols $0\mbox{--}9$)\\
$L_i \perp L_j$ & $L_i$ orthogonal to $L_j$\\
$\cl(A,B)$ & Clash count: symbol pairs missing from superposition\\
$\E$ & Total energy $= \cl_{12}+\cl_{13}+\cl_{23}$\\
$\CT(L_1,L_2)$ & Common transversal count\\
SA & Simulated annealing\\
PT & Parallel tempering\\
ILS & Iterated local search\\
CDCL & Conflict-driven clause learning\\
\bottomrule
\end{tabular}
\end{center}

\bigskip
\noindent\textbf{Data availability.} All near-miss triples, MOLS pairs, worker logs, and
search code are available at \url{https://github.com/ajzhanghk/autoresearch-glm}, branch
\texttt{claude/mols-order-10-search-yfQXK}.

% ===========================================================================
\begin{thebibliography}{99}
% ===========================================================================

\bibitem{audemard2009}
Audemard, G., \& Simon, L. (2009).
Predicting learnt clauses quality in modern SAT solvers.
\textit{Proceedings of IJCAI}, 399--404.

\bibitem{ortools}
Google OR-Tools Team. (2023).
OR-Tools: Google's operations research tools.
\url{https://developers.google.com/optimization}.
Version 9.x, CP-SAT solver.

\bibitem{rc2}
Ignatiev, A., Morgado, A., \& Marques-Silva, J. (2019).
RC2: An efficient MaxSAT solver.
\textit{Journal on Satisfiability, Boolean Modeling and Computation}, 11(1), 53--64.

\bibitem{clements1977}
Clements, G. F., \& Lindstr\"{o}m, B. (1965).
A generalization of a combinatorial theorem of Macaulay.
\textit{Journal of Combinatorial Theory}, 7(3), 230--238.

\bibitem{colbourn2006}
Colbourn, C. J., \& Dinitz, J. H. (Eds.) (2006).
\textit{Handbook of Combinatorial Designs} (2nd ed.).
Chapman \& Hall/CRC.

\bibitem{denes1991}
D\'{e}nes, J., \& Keedwell, A. D. (1991).
\textit{Latin Squares: New Developments in the Theory and Applications}.
North-Holland.

\bibitem{euler1782}
Euler, L. (1782).
Recherches sur une nouvelle esp\`{e}ce de quarr\'{e}s magiques.
\textit{Verhandelingen uitgegeven door het zeeuwsch genootschap der wetenschappen te Vlissingen}, 9, 85--239.

\bibitem{geyer1991}
Geyer, C. J. (1991).
Markov chain Monte Carlo maximum likelihood.
\textit{Proceedings of the 23rd Symposium on the Interface}, 156--163.

\bibitem{knuth2000}
Knuth, D. E. (2000).
Dancing links.
\textit{Millennial Perspectives in Computer Science}, 187--214.

\bibitem{lam1989}
Lam, C. W. H., Thiel, L., \& Swiercz, S. (1989).
The nonexistence of finite projective planes of order 10.
\textit{Canadian Journal of Mathematics}, 41(6), 1117--1123.

\bibitem{mckay2007}
McKay, B. D., Meynert, A., \& Myrvold, W. (2007).
Small Latin squares, quasigroups, and loops.
\textit{Journal of Combinatorial Designs}, 15(2), 98--119.

\bibitem{parker1960}
Parker, E. T. (1960).
Orthogonal Latin squares.
\textit{Proceedings of the National Academy of Sciences}, 47(6), 859--862.

\bibitem{tarry1901}
Tarry, G. (1901).
Le probl\`{e}me des 36 officiers.
\textit{Compte Rendu de l'Association Fran\c{c}aise pour l'Avancement des Sciences Naturelles}, 2, 170--203.

\bibitem{wanless2011}
Wanless, I. M., \& Webb, B. S. (2011).
The existence of Latin squares without orthogonal mates.
\textit{Designs, Codes and Cryptography}, 60(2), 143--151.

\end{thebibliography}

\end{document}
